### 2017-04-05 index.Rmd
new website; mostly complete with some chunks missing.

---
title: "Jeff Goldsmith"
---

<link rel="stylesheet" href="styles.css" type="text/css">

### Assistant Professor of Biostatistics, Columbia University Mailman School of Public Health

<br><img src="jeff.jpg" alt="jeff" style="width:85%; border:10px solid"><br>

I recieved a BS in mathematics from [Dickinson College](http://www.dickinson.edu) in 2007 and a PhD in Biostatistics from [Johns Hopkins University](http://www.jhsph.edu/departments/biostatistics/) in 2012. My dissertation was advised by [Ciprian Crainiceanu](http://www.biostat.jhsph.edu/~ccrainic/) and [Brian Caffo](https://sites.google.com/view/bcaffo/home), and focused on statistical methods for high-dimensional structured data. I joined Columbia as an assistant professor in 2012.

My statistical research is generally focused on functional data analysis, and draws heavily from ongoing collaborations with researchers in other disciplines. One major emphasis is the use of motion kinematics to understand motor control, skill learning, and recovery following stroke; another is physical activity measurement and quantification using wearable devices. The [research](research.html) page has more information on recent projects.

In 2013, I founded (with [Todd Ogden](https://www.mailman.columbia.edu/people/our-faculty/to166) and [Phil Reiss](https://works.bepress.com/phil_reiss/)) the Functional Data Analysis Working Group ([FDAWG](https://www.mailman.columbia.edu/research/functional-data-analysis-working-group)) at Columbia Biostat.

<br>

#### Curriculum Vitae

My full CV is availble [here](Downloads/CV_Goldsmith.pdf).

<br>

#### Contact Information

Jeff Goldsmith  
[Department of Biostatistics](http://www.mailman.columbia.edu/academic-departments/biostatistics)  
[Columbia Mailman School of Public Health](http://www.mailman.columbia.edu/)  
722 West 168th Street, Room 630  
New York, New York 10032

Email: [jeff.goldsmith@olumbia.edu](mailto:jeff.goldsmith@columbia.edu)  
Phone: 212-342-4599

### 2017-04-05 papers.Rmd
new website; mostly complete with some chunks missing.

---
output:
  html_document:
    toc: true
    toc_float: true
---

<link rel="stylesheet" href="styles.css" type="text/css" />

<br>
<font size="5">[Google Scholar Page](https://scholar.google.com/citations?user=3wvmkE0AAAAJ)</font> 
<br>

In the following, <sup>&#8224;</sup> denotes equal contribution and <sup>&#8225;</sup> indicates a student under my supervision.

## 2017

J. C. Cortes<sup>&#8224;</sup>, **J. Goldsmith**<sup>&#8224;</sup>, M. Harran, J. Xu, N. Kim, A. R. Luft, P. Celnik, J. W. Krakauer, and T. Kitago (2017+).
A short and distinct time window for recovery of arm motor control after stroke revealed with a global measure of trajectory kinematics.
<i> Neurorehabilitation and Neural Repair, </i>
accepted.

M. Kronish, K. M. Diaz, **J. Goldsmith**, N. Moise, and J. E. Schwartz.
Objectively measured adherence to physical activity guidelines after acute coronary syndrome (2017+).
<i> Journal of the American College of Cardiology, </i>
accepted.

P. T. Reiss, **J. Goldsmith**, H. L. Shang, R. T. Ogden.
Methods for Scalar-on-Function Regression (2017+).
<i> International Statistical Review, </i>
accepted.

**J. Goldsmith**, J. E. Schwartz.
Variable Selection in the Functional Linear Concurrent Model (2017+).
<i> Statistics in Medicine, </i>
accepted.
[[PDF](Downloads/VBVS.pdf)
| [GitHub](https://github.com/jeff-goldsmith/vbvs.concurrent)]

J. Gertheiss, **J. Goldsmith**, H. L. Shang, A.-M. Staicu (2017).
A note on modeling sparse exponential-family functional response curves.
<i> Computational Statistics and Data Analysis, </i>
<b>105</b> 46-52.
[[Link](http://www.sciencedirect.com/science/article/pii/S0167947316301748) |
[GitHub](https://github.com/jeff-goldsmith/vbvs.concurrent)]

## 2016

A. Castano, M. Haq, D. Narotsky, **J. Goldsmith**, R. L. Weinberg, R. Morgenstern, T. Pozniakoff, F. L. Ruberg, E. J. Miller, J. L. Berk, A. Dispenzieri, M. Grogan, G.
Multicenter Experience of Planar Technetium Pyrophosphate Cardiac Imaging: Does Preferential Cardiac Uptake Predict Survival in Patients with ATTR Cardiac Amyloidosis?
<i> JAMA Cardiology, </i>
<b>1</b> 880-889.

**J. Goldsmith**.
vbvs.concurrent: Fitting Methods for the Functional Linear Concurrent Model (2016).
<i> The Journal of Open Source Software, </i>
<b>1</b>.
[[Link](http://joss.theoj.org/papers/a3884174f17dbb9a695f7b8658887eff) |
[GitHub](https://github.com/jeff-goldsmith/vbvs.concurrent)]

S. T. Sorge, D. C. Hesdorffer, J. C. Phelan, M. R. Winawer, S. Shostak, **J. Goldsmith**, W. K. Chung, R. Ottman (2016).
Genetic causal attribution and depression in multiplex epilepsy families.
<i> Epilepsia, </i>
<b>57</b> 1643-1650.
[[Link](http://onlinelibrary.wiley.com/doi/10.1111/epi.13500/full)
| [PubMed](http://www.ncbi.nlm.nih.gov/pubmed/27558297)]

A. L. Wong, **J. Goldsmith**, J Krakauer (2016).
A motor planning stage represents the shape of upcoming movement trajectories.
<i> Journal of Neurophysiolog, </i>
<b>116</b> 296-305.
[[Link](http://jn.physiology.org/content/116/2/296)
| [PubMed](http://www.ncbi.nlm.nih.gov/pubmed/27098032)]

**J. Goldsmith**, X. Liu<sup>&#8225;</sup>, J. S. Jacobson, A. Rundle (2016).
New insights into activity patterns in children, found using functional data analyses.
<i> Medicine and Science in Sports and Exercise, </i>
<b>48</b> 1723-1729.
[[Link](http://journals.lww.com/acsm-msse/Abstract/2016/09000/New_Insights_into_Activity_Patterns_in_Children,.11.aspx)
| [PDF](Downloads/HeadStart.pdf)
| [Code](Downloads/HeadStartCode.zip)
| [PubMed](http://www.ncbi.nlm.nih.gov/pubmed/27183122)]

J. Wrobel<sup>&#8225;</sup>, S.Y. Park, A.M. Staicu, **J. Goldsmith** (2016).
Interactive graphics for functional data analyses.
<i> Stat, </i>
<b>5</b> 108-118.
[[arXiv](http://arxiv.org/abs/1602.04091)
| [Link](http://onlinelibrary.wiley.com/doi/10.1002/sta4.109/abstract)
| [GitHub](https://github.com/refunders/refund.shiny)
| [CRAN](https://cran.r-project.org/web/packages/refund.shiny/index.html)]

Y. Chen<sup>&#8225;</sup>, **J. Goldsmith**, T. Ogden (2016).
Variable Selection in Function-on-Scalar Regression.
<i> Stat, </i>
<b>5</b> 88-101.
[[Link](http://onlinelibrary.wiley.com/doi/10.1002/sta4.106/abstract)
| [PDF](Downloads/FoS_VarSelect.pdf)
| Implemented in [refund](https://github.com/refunders/refund) as fosr.vs()]

**J. Goldsmith**, T. Kitago (2016).
Assessing Systematic Effects of Stroke on Motor Control using Hierarchical Function-on-Scalar Regression.
<i> Journal of the Royal Statistical Society: Series C, </i>
<b>65</b> 215-236.
[[PDF](Downloads/BayesPFSR_Paper.pdf)
| [Link](http://onlinelibrary.wiley.com/doi/10.1111/rssc.12115/abstract)
| [Code](Downloads/BayesPFSR_Code.zip)
| [Shiny App](https://jeff-goldsmith.shinyapps.io/MotorControl_Interactive)]

C. B. Caminiti, D. C. Hesdorffer, S. Shostak, **J. Goldsmith**, S. T. Sorge, M. R. Winawer, J. C. Phelan, W. K. Chung, and R. Ottman (2016).
Parents' interest in genetic testing of their offspring in multiplex epilepsy families.
<i> Epilepsia, </i>
<b>57</b> 279-287.
[[Link](http://onlinelibrary.wiley.com/doi/10.1111/epi.13287/abstract)
| [PubMed](http://www.ncbi.nlm.nih.gov/pubmed/26693851)]

K. M. Diaz, D. J Krupka, M. J. Chang, J. A. Schaffer, Y. Ma, **J. Goldsmith**, J. E. Schwartz, K. W. Davidson (2016).
Validation of the Fitbit One for physical activity measurement at an upper torso attachment site.
<i> BMC Research Notes, </i>
<b>9</b> 213.
[[Link](http://bmcresnotes.biomedcentral.com/articles/10.1186/s13104-016-2020-8)
| [PubMed](http://www.ncbi.nlm.nih.gov/pubmed/27068022)]

M. Abdalla, **J. Goldsmith**, P. Muntner, K. M. Diaz, K. Reynolds, J. E. Schwartz, D. Shimbo (2016).
Is Isolated Nocturnal Hypertension a Reproducible Phenotype?
<i> American Journal of Hypertension, </i>
<b>29</b> 33-38.
[[Link](http://ajh.oxfordjournals.org/content/29/1/33.full.pdf+html)
| [PubMed](http://www.ncbi.nlm.nih.gov/pubmed/25904648)]

## 2015

T. Kitago<sup>&#8224;</sup>, **J. Goldsmith**<sup>&#8224;</sup>, M. Harran, L. Kane, J. Berard, S. Huang, S. Ryan, P. Mazzoni, J, Krakauer, and V. Huang (2015).
Robotic therapy for chronic stroke: general recovery of impairment or improved task-specific skill?
<i> Journal of Neurophysiology, </i>
<b>114</b> 1885-1894.
[[Link](http://jn.physiology.org/content/early/2015/07/10/jn.00336.2015.abstract)
| [PubMed](http://www.ncbi.nlm.nih.gov/pubmed/26032276)]
(&#8224; denotes equal contribution)

**J. Goldsmith**, V. Zipunnikov, J. Schrack (2015).
Generalized Multilevel Functional-on-Scalar Regression and Principal Component Analysis.
<i> Biometrics, </i>
<b>71</b> 344-353.
[[Link](http://onlinelibrary.wiley.com/doi/10.1111/biom.12278/abstract)
| [PubMed](http://www.ncbi.nlm.nih.gov/pubmed/25620473)
| [Code](Downloads/GenMFPCA_Code.zip)
| [Shiny App](https://jeff-goldsmith.shinyapps.io/GFPCA_interactive)]

U. M. Schambra, **J. Goldsmith**, H. M. Schambra, K. Nunleya, S. Harirforoosh, Y. Liu , and S. S. Moy (2015).
Low and moderate prenatal ethanol exposure of mice during gastrulation or neurulation delays neurobehavioral development.
<i> Neurotoxicology and Teratology, </i>
<b>51</b> 1-11.
[[Link](http://www.sciencedirect.com/science/article/pii/S089203621530012X)
| [PubMed](http://www.ncbi.nlm.nih.gov/pubmed/26171567)]

K. M. Diaz, D. J Krupka, M. J. Chang, J. Peacock, Y. Ma, **J. Goldsmith**, J. E. Schwartz, K. W. Davidson (2015).
Fitbit: An accurate and reliable device for wireless physical activity tracking.
<i> International Journal of Cardiology, </i>
<b>185</b> 138-140.
[[Link](http://www.internationaljournalofcardiology.com/article/S0167-5273(15)00276-4/abstract)
| [PubMed](http://www.ncbi.nlm.nih.gov/pubmed/25795203)]

C. Wang, S. Vine, A. Hsiao, A. Rundle, and **J. Goldsmith** (2015).
Weight-Related Behaviors When Children are in School Versus on Summer Breaks: Does Income Matter?
<i> Journal of School Health, </i>
<b>85</b> 458-466.
[[Link](http://onlinelibrary.wiley.com/doi/10.1111/josh.12274/abstract)
| [PubMed](http://www.ncbi.nlm.nih.gov/pubmed/26032276)]

M. Sabatello, J. Phelan, D. C. Hesdorffer, S. Shostak, **J. Goldsmith**, S. Sorge, M. Winawer, W. Chung, R. Ottman (2015).
Genetic Causal Attribution of Epilepsy and its Implications for Felt Stigma.
<i> Epilepsia, </i>
<b>56</b> 1542-1550.
[[Link](http://onlinelibrary.wiley.com/doi/10.1111/epi.13113/abstract)
| [PubMed](http://www.ncbi.nlm.nih.gov/pubmed/26290354)]

## 2014

**J. Goldsmith**, L. Huang, C. M. Crainiceanu (2014).
Smooth Scalar-on-Image Regression via Spatial Bayesian Variable Selection.
<i> Journal of Computational and Graphical Statistics, </i>
<b>23</b> 46-64.
[[Link](http://amstat.tandfonline.com/doi/abs/10.1080/10618600.2012.743437#.U2pt-17A7d4) |
[PubMed](http://www.ncbi.nlm.nih.gov/pubmed/24729670)]

**J. Goldsmith**, F. Scheipl (2014).
Estimator Selection and Combination in Scalar-on-Function Regression.
<i> Computational Statistics and Data Analysis, </i>
<b>70</b> 362-372.
[[Link](http://www.sciencedirect.com/science/article/pii/S0167947313003629) |
[PDF](Downloads/Ensembling_Paper.pdf) |
[Code](Downloads/Ensembling_Code.zip)]

J. A. Schrack, V. Zipunnikov, **J. Goldsmith**, K. Bandeen-Roche, C. M. Crainiceanu, L. Ferrucci (2014).
Estimating Energy Expenditure from Heart Rate in Older Adults: a Case for Calibration.
<i> PLoS One, </i>
<b>9</b> 1-9.
[[Link](http://www.plosone.org/article/info%3Adoi%2F10.1371%2Fjournal.pone.0093520) |
[PubMed](http://www.ncbi.nlm.nih.gov/pubmed/24787146)]

J. A. Schrack, V. Zipunnikov, **J. Goldsmith**, J. Bai, E. M. Simonsick, C. M. Crainiceanu, L. Ferrucci (2014).
Assessing the "Physical Cliff": Detailed Quantification of Aging and Physical Activity.
<i> Journal of Gerontology: Medical Sciences. </i>
<b>69</b> 973-979.
[[Link](http://biomedgerontology.oxfordjournals.org/content/69/8/973.full.pdf) |
[PubMed](http://www.ncbi.nlm.nih.gov/pubmed/24336819) |
Article selected as "Editor's Choice"]

S. Vullaganti, **J. Goldsmith**, S. Teruya, J. Alvarez, S. Helmke, M. Maurer (2014).
Cardiovascular effects of hemoglobin response in patients receiving epoetin alfa and oral iron in heart failure with a preserved ejection fraction.
<i> Journal of Geriatric Cardiology, </i>
<b>11</b> 100-105.
[[Link](http://www.jgc301.com/ch/reader/view_abstract.aspx?file_no=20140227001&flag=1)
| [PubMed](http://www.ncbi.nlm.nih.gov/pubmed/25009558)]

B. Swihart, **J. Goldsmith**, C. M. Crainiceanu. (2014).
Restricted Likelihood Ratio Tests for Functional Effects in the Functional Linear Model.
<i> Technometrics, </i>
<b>56</b> 483-493.
[[Link](http://www.tandfonline.com/doi/full/10.1080/00401706.2013.863163)]

A. Hauschild, S. C. Chen, M. Weichenthal, A. Blum, H. C. King, **J. Goldsmith**, D. O. Scharfstein, D. Gutkowicz-Krusin (2014).
To excise or not: impact of MelaFind on German dermatologists' decisions to biopsy atypical lesions.
<i>JDDG: Journal der Deutschen Dermatologischen Gesellschaft, </i>
<b>12</b> 606-614.
[[Link](http://onlinelibrary.wiley.com/doi/10.1111/ddg.12362/abstract) |
[PubMed](http://www.ncbi.nlm.nih.gov/pubmed/24944011)]

J. O. Okeke, V. E. Tangel, S. T. Sorge, D. C. Hesdorffer, M. R. Winawer, **J. Goldsmith**, J. Phelan, W. Chung, S. Shostak, R. Ottman (2014).
Genetic Testing Preferences in Families Containing Multiple Individuals with Epilepsy.
<i>Epilepsia, </i>
<b>55</b> 1705-1713.
[[Link](http://onlinelibrary.wiley.com/doi/10.1111/epi.12810/full) |
[PubMed](http://www.ncbi.nlm.nih.gov/pubmed/25266816)]

G. S. Lovasi, **J. Goldsmith** (2014).
Invited commentary: Taking advantage of time-varying neighborhood environments.
<i>American Journal of Epidemiology, </i>
<b>DOI:</b> 10.1093/aje/kwu170.
[[Link](http://aje.oxfordjournals.org/content/180/5/462.full) |
[PubMed](http://www.ncbi.nlm.nih.gov/pubmed/25117659)]

N. Cyrille, **J. Goldsmith**, J. Alvarez, M. S. Maurer (2014).
Prevalence and Prognostic Significance of Low QRS Voltage Among the Three Main Types of Cardiac Amyloid.
<i> American Journal of Cardiology, </i>
<b>114</b> 1089-1093.
[[Link](http://www.sciencedirect.com/science/article/pii/S0002914914014544#) |
[PubMed](http://www.ncbi.nlm.nih.gov/pubmed/25212550)]

R. T. Shinohara, E. M. Sweeny, **J. Goldsmith**, N. Shiee, F. J. Mateen, P. A. Calabresi, S. Jarso, D. L. Pham, D. S. Reich, C. M. Crainiceanu (2014).
Statistical Normalization Techniques for Magnetic Resonance Imaging.
<i> NeuroImage: Clinical, </i>
<b>6</b> 9-19
[[Link](http://www.sciencedirect.com/science/article/pii/S221315821400117X#) |
[PubMed](http://www.ncbi.nlm.nih.gov/pubmed/25379412)]

## 2013

**J. Goldsmith**, S. Greven, C. M. Crainiceanu (2013).
Corrected Confidence Bands for Functional Data Using Principal Components.
<i> Biometrics, </i>
<b>69</b> 41-51.
[[Link](http://onlinelibrary.wiley.com/doi/10.1111/j.1541-0420.2012.01808.x/abstract) |
[PubMed](http://www.ncbi.nlm.nih.gov/pubmed/23003003)]

J. Gertheiss, **J. Goldsmith**, C. M. Crainiceanu, S. Greven. (2013).
Longitudinal Scalar-on-Functions Regression with Application to Tractography Data.
	<i> Biostatistics. </i>
<b>14</b> 447-461.
[[Link](http://biostatistics.oxfordjournals.org/content/14/3/447.long) |
[PubMed](http://www.ncbi.nlm.nih.gov/pubmed/23292804)]

H. Sorensen, **J. Goldsmith**, L. Sangalli. (2013).
An Introduction with Medical Applications to Functional Data Analysis.
<i> Statistics in Medicine. </i>
<b>32</b> 5222-5240.
[[Link](http://www.tandfonline.com/doi/abs/10.1080/10618600.2012.679241) |
[PubMed](http://www.ncbi.nlm.nih.gov/pubmed/23794794)]

L. Huang, **J. Goldsmith**, P. T. Reiss, D. S. Reich, C. M. Crainiceanu. (2013).
Bayesian Scalar-on-Image Regression with Application to Association Between Intracranial DTI and Cognitive Outcomes.
<i> NeuroImage. </i>
<b>83</b> 210-223.
[[Link](http://www.sciencedirect.com/science/article/pii/S1053811913006575) |
[PubMed](http://www.ncbi.nlm.nih.gov/pubmed/23792220)]

F. J. Leyva, R. P. Bakshi, E. J. Fuchs, L. Li, B. S. Caffo, **J. Goldsmith**, Y. Du, J. P. Leal, L. A. Lee, M. S. Torbenson, C. W. Hendrix (2013).
Iso-osmolar enemas demonstrate preferential gastrointestinal distribution, safety, and acceptability compared with hyper- and hypo-osmolar enemas as a potential delive
<i> AIDS Research and Human Retroviruses. </i>
<b>29</b> 1487-1495.
[[Link](http://online.liebertpub.com/doi/abs/10.1089/aid.2013.0189) |
[PubMed](http://www.ncbi.nlm.nih.gov/pubmed/23885722)]

## 2012

**J. Goldsmith**, C. M. Crainiceanu, B. S. Caffo, D. S. Reich (2012).
Longitudinal Penalized Functional Regression for Cognitive Outcomes on Neuronal Tract Measurements.
<i> Journal of the Royal Statistical Society: Series C, </i>
<b>61</b> 453-469.
[[Link](http://onlinelibrary.wiley.com/doi/10.1111/j.1467-9876.2011.01031.x/abstract) |
[PubMed](http://www.ncbi.nlm.nih.gov/pubmed/22679339) |
[Simulation Code](Downloads/LPFR_Code.zip)]

T. Shinohara, **J. Goldsmith**, F. Mateen, D. S. Reich, C. M. Crainiceanu (2012).
Predicting Breakdown of the Blood-Brain Barrier in Multiple Sclerosis Without Contrast Agents.
<i> American Journal of Neuroradiology, </i>
<b>33</b> 1586-1590.
[[Link](http://www.ajnr.org/content/33/8/1586.long) |
[PubMed](http://www.ncbi.nlm.nih.gov/pubmed/22442041)]

J. Bai, **J. Goldsmith**, B. S. Caffo, T. Glass, C. M. Crainiceanu (2012).
Movelets: A Dictionary of Movement.
<i> Electronic Journal of Statistics, </i>
<b>6</b> 559-578.
[[Link](https://projecteuclid.org/euclid.ejs/1334065322) |
[PubMed](http://www.ncbi.nlm.nih.gov/pubmed/23293708)]

N. Louissant, S. Nimmagadda, R. Bakshi, Y. Du, K. Macura, K. King, R. Wahl, **J. Goldsmith**, B. S. Caffo,
Y.-J. Cao, J. Anderson, E. Fuchs, C. W. Hendrix (2012).
Distribution of Cell-free and Cell-associated HIV Surrogates in the Female Genital Tract following Simulated Vaginal Intercourse.
<i> Journal of Infectious Diseases, </i>
<b>205</b> 725-732.
[[Link](http://jid.oxfordjournals.org/content/205/5/725) |
[PubMed](http://www.ncbi.nlm.nih.gov/pubmed/22279121)]

N. Louissant, S. Nimmagadda, E. Fuchs, R. Bakshi, Y. Cao, L. Lee, **J. Goldsmith**, B. S. Caffo, Y. Du, K. King,
F. Menendez, M. Torbenson, C. W. Hendrix (2012).
Distribution of Cell-free and Cell-associated HIV Surrogates in the Colon following Simulated Receptive Anal Intercourse.
<i> Journal of Acquired Immune Deficiency Syndromes, Basic and Translational Science, </i>
<b>59</b> 10-17.
[[Link](http://ovidsp.tx.ovid.com/sp-3.12.0b/ovidweb.cgi?&S=KOLDFPPIPMDDFJDMNCMKNBLBBJIDAA00&Link+Set=S.sh.27.28.32.42%7c2%7csl_10) |
[PubMed](http://www.ncbi.nlm.nih.gov/pubmed/21937920)]

## 2011 and before

**J. Goldsmith**, J. Bobb, C. M. Crainiceanu, B. S. Caffo, D. S. Reich (2011).
Penalized Functional Regression.
<i> Journal of Computational and Graphical Statistics, </i>
<b>20</b> 830-851.
[[Link](http://www.tandfonline.com/doi/abs/10.1198/jcgs.2010.10007#.U1BzC16ft94) |
[PubMed](http://www.ncbi.nlm.nih.gov/pubmed/22368438) |
[Simulation Code](Downloads/PFR_Code.zip)]

**J. Goldsmith**, C. M. Crainiceanu, B. S. Caffo, D. S. Reich (2011).
Penalized Functional Regression Analysis of White-Matter Tract Profiles in Multiple Sclerosis.
<i> NeuroImage, </i>
<b>57</b> 431-439.
[[Link](http://www.sciencedirect.com/science/article/pii/S1053811911004435) |
[PubMed](http://www.ncbi.nlm.nih.gov/pubmed/21554962)]

**J. Goldsmith**, B. S. Caffo, C. M. Crainiceanu, D. Reich, Y. Du, C. W. Hendrix (2011).
Nonlinear Tube-Fitting for the Analysis of Anatomical and Functional Structures.
<i> Annals of Applied Statistics, </i>
<b>5</b> 337-363.
[[Link](http://projecteuclid.org/euclid.aoas/1300715193) |
[PubMed](http://www.ncbi.nlm.nih.gov/pubmed/21709824)]

**J. Goldsmith**, M. P. Wand, and C. M. Crainiceanu (2011).
Functional Regression via Variational Bayes.
<i> Electronic Journal of Statistics, </i>
<b>5</b> 572-602.
[[Link](http://projecteuclid.org/euclid.ejs/1308143123) |
[PubMed](http://www.ncbi.nlm.nih.gov/pubmed/22163061) |
[Simulation Code](Downloads/VB_Code.zip)]

C. M. Crainiceanu, **J. Goldsmith** (2010).
Bayesian Functional Data Analysis using WinBUGS.
<i> Journal of Statistical Software, </i>
<b>32</b> 1-33.
[[Link](http://www.jstatsoft.org/v32/i11/) |
[PubMed](http://www.ncbi.nlm.nih.gov/pubmed/21743798)]

**J. Goldsmith**, L. Koss (2009).
Dynamical Properties of the Derivative of the Weierstrass Elliptic Function.
<i> Involve, </i>
<b>2</b> 267-288.
[[Link](http://msp.org/involve/2009/2-3/p02.xhtml) |
[pdf](Downloads/Weierstrass.pdf)]

### 2017-04-05 research.Rmd
new website; mostly complete with some chunks missing.

--- 2017-04-05 papers.Rmd
@@
 ---
-output:
-  html_document:
-    toc: true
-    toc_float: true
+title: "Jeff Goldsmith"
 ---
@@
 
-<br>
-<font size="5">[Google Scholar Page](https://scholar.google.com/citations?user=3wvmkE0AAAAJ)</font> 
-<br>
+## Motion kinematics
 
-In the following, <sup>&#8224;</sup> denotes equal contribution and <sup>&#8225;</sup> indicates a student under my supervision.
+(text placeholder)
 
-## 2017
+## Wearable devices
 
-J. C. Cortes<sup>&#8224;</sup>, **J. Goldsmith**<sup>&#8224;</sup>, M. Harran, J. Xu, N. Kim, A. R. Luft, P. Celnik, J. W. Krakauer, and T. Kitago (2017+).
-A short and distinct time window for recovery of arm motor control after stroke revealed with a global measure of trajectory kinematics.
-<i> Neurorehabilitation and Neural Repair, </i>
-accepted.
-
-M. Kronish, K. M. Diaz, **J. Goldsmith**, N. Moise, and J. E. Schwartz.
-Objectively measured adherence to physical activity guidelines after acute coronary syndrome (2017+).
-<i> Journal of the American College of Cardiology, </i>
-accepted.
-
-P. T. Reiss, **J. Goldsmith**, H. L. Shang, R. T. Ogden.
-Methods for Scalar-on-Function Regression (2017+).
-<i> International Statistical Review, </i>
-accepted.
-
-**J. Goldsmith**, J. E. Schwartz.
-Variable Selection in the Functional Linear Concurrent Model (2017+).
-<i> Statistics in Medicine, </i>
-accepted.
-[[PDF](Downloads/VBVS.pdf)
-| [GitHub](https://github.com/jeff-goldsmith/vbvs.concurrent)]
-
-J. Gertheiss, **J. Goldsmith**, H. L. Shang, A.-M. Staicu (2017).
-A note on modeling sparse exponential-family functional response curves.
-<i> Computational Statistics and Data Analysis, </i>
-<b>105</b> 46-52.
-[[Link](http://www.sciencedirect.com/science/article/pii/S0167947316301748) |
-[GitHub](https://github.com/jeff-goldsmith/vbvs.concurrent)]
-
-## 2016
-
-A. Castano, M. Haq, D. Narotsky, **J. Goldsmith**, R. L. Weinberg, R. Morgenstern, T. Pozniakoff, F. L. Ruberg, E. J. Miller, J. L. Berk, A. Dispenzieri, M. Grogan, G.
-Multicenter Experience of Planar Technetium Pyrophosphate Cardiac Imaging: Does Preferential Cardiac Uptake Predict Survival in Patients with ATTR Cardiac Amyloidosis?
-<i> JAMA Cardiology, </i>
-<b>1</b> 880-889.
-
-**J. Goldsmith**.
-vbvs.concurrent: Fitting Methods for the Functional Linear Concurrent Model (2016).
-<i> The Journal of Open Source Software, </i>
-<b>1</b>.
-[[Link](http://joss.theoj.org/papers/a3884174f17dbb9a695f7b8658887eff) |
-[GitHub](https://github.com/jeff-goldsmith/vbvs.concurrent)]
-
-S. T. Sorge, D. C. Hesdorffer, J. C. Phelan, M. R. Winawer, S. Shostak, **J. Goldsmith**, W. K. Chung, R. Ottman (2016).
-Genetic causal attribution and depression in multiplex epilepsy families.
-<i> Epilepsia, </i>
-<b>57</b> 1643-1650.
-[[Link](http://onlinelibrary.wiley.com/doi/10.1111/epi.13500/full)
-| [PubMed](http://www.ncbi.nlm.nih.gov/pubmed/27558297)]
-
-A. L. Wong, **J. Goldsmith**, J Krakauer (2016).
-A motor planning stage represents the shape of upcoming movement trajectories.
-<i> Journal of Neurophysiolog, </i>
-<b>116</b> 296-305.
-[[Link](http://jn.physiology.org/content/116/2/296)
-| [PubMed](http://www.ncbi.nlm.nih.gov/pubmed/27098032)]
-
-**J. Goldsmith**, X. Liu<sup>&#8225;</sup>, J. S. Jacobson, A. Rundle (2016).
-New insights into activity patterns in children, found using functional data analyses.
-<i> Medicine and Science in Sports and Exercise, </i>
-<b>48</b> 1723-1729.
-[[Link](http://journals.lww.com/acsm-msse/Abstract/2016/09000/New_Insights_into_Activity_Patterns_in_Children,.11.aspx)
-| [PDF](Downloads/HeadStart.pdf)
-| [Code](Downloads/HeadStartCode.zip)
-| [PubMed](http://www.ncbi.nlm.nih.gov/pubmed/27183122)]
-
-J. Wrobel<sup>&#8225;</sup>, S.Y. Park, A.M. Staicu, **J. Goldsmith** (2016).
-Interactive graphics for functional data analyses.
-<i> Stat, </i>
-<b>5</b> 108-118.
-[[arXiv](http://arxiv.org/abs/1602.04091)
-| [Link](http://onlinelibrary.wiley.com/doi/10.1002/sta4.109/abstract)
-| [GitHub](https://github.com/refunders/refund.shiny)
-| [CRAN](https://cran.r-project.org/web/packages/refund.shiny/index.html)]
-
-Y. Chen<sup>&#8225;</sup>, **J. Goldsmith**, T. Ogden (2016).
-Variable Selection in Function-on-Scalar Regression.
-<i> Stat, </i>
-<b>5</b> 88-101.
-[[Link](http://onlinelibrary.wiley.com/doi/10.1002/sta4.106/abstract)
-| [PDF](Downloads/FoS_VarSelect.pdf)
-| Implemented in [refund](https://github.com/refunders/refund) as fosr.vs()]
-
-**J. Goldsmith**, T. Kitago (2016).
-Assessing Systematic Effects of Stroke on Motor Control using Hierarchical Function-on-Scalar Regression.
-<i> Journal of the Royal Statistical Society: Series C, </i>
-<b>65</b> 215-236.
-[[PDF](Downloads/BayesPFSR_Paper.pdf)
-| [Link](http://onlinelibrary.wiley.com/doi/10.1111/rssc.12115/abstract)
-| [Code](Downloads/BayesPFSR_Code.zip)
-| [Shiny App](https://jeff-goldsmith.shinyapps.io/MotorControl_Interactive)]
-
-C. B. Caminiti, D. C. Hesdorffer, S. Shostak, **J. Goldsmith**, S. T. Sorge, M. R. Winawer, J. C. Phelan, W. K. Chung, and R. Ottman (2016).
-Parents' interest in genetic testing of their offspring in multiplex epilepsy families.
-<i> Epilepsia, </i>
-<b>57</b> 279-287.
-[[Link](http://onlinelibrary.wiley.com/doi/10.1111/epi.13287/abstract)
-| [PubMed](http://www.ncbi.nlm.nih.gov/pubmed/26693851)]
-
-K. M. Diaz, D. J Krupka, M. J. Chang, J. A. Schaffer, Y. Ma, **J. Goldsmith**, J. E. Schwartz, K. W. Davidson (2016).
-Validation of the Fitbit One for physical activity measurement at an upper torso attachment site.
-<i> BMC Research Notes, </i>
-<b>9</b> 213.
-[[Link](http://bmcresnotes.biomedcentral.com/articles/10.1186/s13104-016-2020-8)
-| [PubMed](http://www.ncbi.nlm.nih.gov/pubmed/27068022)]
-
-M. Abdalla, **J. Goldsmith**, P. Muntner, K. M. Diaz, K. Reynolds, J. E. Schwartz, D. Shimbo (2016).
-Is Isolated Nocturnal Hypertension a Reproducible Phenotype?
-<i> American Journal of Hypertension, </i>
-<b>29</b> 33-38.
-[[Link](http://ajh.oxfordjournals.org/content/29/1/33.full.pdf+html)
-| [PubMed](http://www.ncbi.nlm.nih.gov/pubmed/25904648)]
-
-## 2015
-
-T. Kitago<sup>&#8224;</sup>, **J. Goldsmith**<sup>&#8224;</sup>, M. Harran, L. Kane, J. Berard, S. Huang, S. Ryan, P. Mazzoni, J, Krakauer, and V. Huang (2015).
-Robotic therapy for chronic stroke: general recovery of impairment or improved task-specific skill?
-<i> Journal of Neurophysiology, </i>
-<b>114</b> 1885-1894.
-[[Link](http://jn.physiology.org/content/early/2015/07/10/jn.00336.2015.abstract)
-| [PubMed](http://www.ncbi.nlm.nih.gov/pubmed/26032276)]
-(&#8224; denotes equal contribution)
-
-**J. Goldsmith**, V. Zipunnikov, J. Schrack (2015).
-Generalized Multilevel Functional-on-Scalar Regression and Principal Component Analysis.
-<i> Biometrics, </i>
-<b>71</b> 344-353.
-[[Link](http://onlinelibrary.wiley.com/doi/10.1111/biom.12278/abstract)
-| [PubMed](http://www.ncbi.nlm.nih.gov/pubmed/25620473)
-| [Code](Downloads/GenMFPCA_Code.zip)
-| [Shiny App](https://jeff-goldsmith.shinyapps.io/GFPCA_interactive)]
-
-U. M. Schambra, **J. Goldsmith**, H. M. Schambra, K. Nunleya, S. Harirforoosh, Y. Liu , and S. S. Moy (2015).
-Low and moderate prenatal ethanol exposure of mice during gastrulation or neurulation delays neurobehavioral development.
-<i> Neurotoxicology and Teratology, </i>
-<b>51</b> 1-11.
-[[Link](http://www.sciencedirect.com/science/article/pii/S089203621530012X)
-| [PubMed](http://www.ncbi.nlm.nih.gov/pubmed/26171567)]
-
-K. M. Diaz, D. J Krupka, M. J. Chang, J. Peacock, Y. Ma, **J. Goldsmith**, J. E. Schwartz, K. W. Davidson (2015).
-Fitbit: An accurate and reliable device for wireless physical activity tracking.
-<i> International Journal of Cardiology, </i>
-<b>185</b> 138-140.
-[[Link](http://www.internationaljournalofcardiology.com/article/S0167-5273(15)00276-4/abstract)
-| [PubMed](http://www.ncbi.nlm.nih.gov/pubmed/25795203)]
-
-C. Wang, S. Vine, A. Hsiao, A. Rundle, and **J. Goldsmith** (2015).
-Weight-Related Behaviors When Children are in School Versus on Summer Breaks: Does Income Matter?
-<i> Journal of School Health, </i>
-<b>85</b> 458-466.
-[[Link](http://onlinelibrary.wiley.com/doi/10.1111/josh.12274/abstract)
-| [PubMed](http://www.ncbi.nlm.nih.gov/pubmed/26032276)]
-
-M. Sabatello, J. Phelan, D. C. Hesdorffer, S. Shostak, **J. Goldsmith**, S. Sorge, M. Winawer, W. Chung, R. Ottman (2015).
-Genetic Causal Attribution of Epilepsy and its Implications for Felt Stigma.
-<i> Epilepsia, </i>
-<b>56</b> 1542-1550.
-[[Link](http://onlinelibrary.wiley.com/doi/10.1111/epi.13113/abstract)
-| [PubMed](http://www.ncbi.nlm.nih.gov/pubmed/26290354)]
-
-## 2014
-
-**J. Goldsmith**, L. Huang, C. M. Crainiceanu (2014).
-Smooth Scalar-on-Image Regression via Spatial Bayesian Variable Selection.
-<i> Journal of Computational and Graphical Statistics, </i>
-<b>23</b> 46-64.
-[[Link](http://amstat.tandfonline.com/doi/abs/10.1080/10618600.2012.743437#.U2pt-17A7d4) |
-[PubMed](http://www.ncbi.nlm.nih.gov/pubmed/24729670)]
-
-**J. Goldsmith**, F. Scheipl (2014).
-Estimator Selection and Combination in Scalar-on-Function Regression.
-<i> Computational Statistics and Data Analysis, </i>
-<b>70</b> 362-372.
-[[Link](http://www.sciencedirect.com/science/article/pii/S0167947313003629) |
-[PDF](Downloads/Ensembling_Paper.pdf) |
-[Code](Downloads/Ensembling_Code.zip)]
-
-J. A. Schrack, V. Zipunnikov, **J. Goldsmith**, K. Bandeen-Roche, C. M. Crainiceanu, L. Ferrucci (2014).
-Estimating Energy Expenditure from Heart Rate in Older Adults: a Case for Calibration.
-<i> PLoS One, </i>
-<b>9</b> 1-9.
-[[Link](http://www.plosone.org/article/info%3Adoi%2F10.1371%2Fjournal.pone.0093520) |
-[PubMed](http://www.ncbi.nlm.nih.gov/pubmed/24787146)]
-
-J. A. Schrack, V. Zipunnikov, **J. Goldsmith**, J. Bai, E. M. Simonsick, C. M. Crainiceanu, L. Ferrucci (2014).
-Assessing the "Physical Cliff": Detailed Quantification of Aging and Physical Activity.
-<i> Journal of Gerontology: Medical Sciences. </i>
-<b>69</b> 973-979.
-[[Link](http://biomedgerontology.oxfordjournals.org/content/69/8/973.full.pdf) |
-[PubMed](http://www.ncbi.nlm.nih.gov/pubmed/24336819) |
-Article selected as "Editor's Choice"]
-
-S. Vullaganti, **J. Goldsmith**, S. Teruya, J. Alvarez, S. Helmke, M. Maurer (2014).
-Cardiovascular effects of hemoglobin response in patients receiving epoetin alfa and oral iron in heart failure with a preserved ejection fraction.
-<i> Journal of Geriatric Cardiology, </i>
-<b>11</b> 100-105.
-[[Link](http://www.jgc301.com/ch/reader/view_abstract.aspx?file_no=20140227001&flag=1)
-| [PubMed](http://www.ncbi.nlm.nih.gov/pubmed/25009558)]
-
-B. Swihart, **J. Goldsmith**, C. M. Crainiceanu. (2014).
-Restricted Likelihood Ratio Tests for Functional Effects in the Functional Linear Model.
-<i> Technometrics, </i>
-<b>56</b> 483-493.
-[[Link](http://www.tandfonline.com/doi/full/10.1080/00401706.2013.863163)]
-
-A. Hauschild, S. C. Chen, M. Weichenthal, A. Blum, H. C. King, **J. Goldsmith**, D. O. Scharfstein, D. Gutkowicz-Krusin (2014).
-To excise or not: impact of MelaFind on German dermatologists' decisions to biopsy atypical lesions.
-<i>JDDG: Journal der Deutschen Dermatologischen Gesellschaft, </i>
-<b>12</b> 606-614.
-[[Link](http://onlinelibrary.wiley.com/doi/10.1111/ddg.12362/abstract) |
-[PubMed](http://www.ncbi.nlm.nih.gov/pubmed/24944011)]
-
-J. O. Okeke, V. E. Tangel, S. T. Sorge, D. C. Hesdorffer, M. R. Winawer, **J. Goldsmith**, J. Phelan, W. Chung, S. Shostak, R. Ottman (2014).
-Genetic Testing Preferences in Families Containing Multiple Individuals with Epilepsy.
-<i>Epilepsia, </i>
-<b>55</b> 1705-1713.
-[[Link](http://onlinelibrary.wiley.com/doi/10.1111/epi.12810/full) |
-[PubMed](http://www.ncbi.nlm.nih.gov/pubmed/25266816)]
-
-G. S. Lovasi, **J. Goldsmith** (2014).
-Invited commentary: Taking advantage of time-varying neighborhood environments.
-<i>American Journal of Epidemiology, </i>
-<b>DOI:</b> 10.1093/aje/kwu170.
-[[Link](http://aje.oxfordjournals.org/content/180/5/462.full) |
-[PubMed](http://www.ncbi.nlm.nih.gov/pubmed/25117659)]
-
-N. Cyrille, **J. Goldsmith**, J. Alvarez, M. S. Maurer (2014).
-Prevalence and Prognostic Significance of Low QRS Voltage Among the Three Main Types of Cardiac Amyloid.
-<i> American Journal of Cardiology, </i>
-<b>114</b> 1089-1093.
-[[Link](http://www.sciencedirect.com/science/article/pii/S0002914914014544#) |
-[PubMed](http://www.ncbi.nlm.nih.gov/pubmed/25212550)]
-
-R. T. Shinohara, E. M. Sweeny, **J. Goldsmith**, N. Shiee, F. J. Mateen, P. A. Calabresi, S. Jarso, D. L. Pham, D. S. Reich, C. M. Crainiceanu (2014).
-Statistical Normalization Techniques for Magnetic Resonance Imaging.
-<i> NeuroImage: Clinical, </i>
-<b>6</b> 9-19
-[[Link](http://www.sciencedirect.com/science/article/pii/S221315821400117X#) |
-[PubMed](http://www.ncbi.nlm.nih.gov/pubmed/25379412)]
-
-## 2013
-
-**J. Goldsmith**, S. Greven, C. M. Crainiceanu (2013).
-Corrected Confidence Bands for Functional Data Using Principal Components.
-<i> Biometrics, </i>
-<b>69</b> 41-51.
-[[Link](http://onlinelibrary.wiley.com/doi/10.1111/j.1541-0420.2012.01808.x/abstract) |
-[PubMed](http://www.ncbi.nlm.nih.gov/pubmed/23003003)]
-
-J. Gertheiss, **J. Goldsmith**, C. M. Crainiceanu, S. Greven. (2013).
-Longitudinal Scalar-on-Functions Regression with Application to Tractography Data.
-	<i> Biostatistics. </i>
-<b>14</b> 447-461.
-[[Link](http://biostatistics.oxfordjournals.org/content/14/3/447.long) |
-[PubMed](http://www.ncbi.nlm.nih.gov/pubmed/23292804)]
-
-H. Sorensen, **J. Goldsmith**, L. Sangalli. (2013).
-An Introduction with Medical Applications to Functional Data Analysis.
-<i> Statistics in Medicine. </i>
-<b>32</b> 5222-5240.
-[[Link](http://www.tandfonline.com/doi/abs/10.1080/10618600.2012.679241) |
-[PubMed](http://www.ncbi.nlm.nih.gov/pubmed/23794794)]
-
-L. Huang, **J. Goldsmith**, P. T. Reiss, D. S. Reich, C. M. Crainiceanu. (2013).
-Bayesian Scalar-on-Image Regression with Application to Association Between Intracranial DTI and Cognitive Outcomes.
-<i> NeuroImage. </i>
-<b>83</b> 210-223.
-[[Link](http://www.sciencedirect.com/science/article/pii/S1053811913006575) |
-[PubMed](http://www.ncbi.nlm.nih.gov/pubmed/23792220)]
-
-F. J. Leyva, R. P. Bakshi, E. J. Fuchs, L. Li, B. S. Caffo, **J. Goldsmith**, Y. Du, J. P. Leal, L. A. Lee, M. S. Torbenson, C. W. Hendrix (2013).
-Iso-osmolar enemas demonstrate preferential gastrointestinal distribution, safety, and acceptability compared with hyper- and hypo-osmolar enemas as a potential delive
-<i> AIDS Research and Human Retroviruses. </i>
-<b>29</b> 1487-1495.
-[[Link](http://online.liebertpub.com/doi/abs/10.1089/aid.2013.0189) |
-[PubMed](http://www.ncbi.nlm.nih.gov/pubmed/23885722)]
-
-## 2012
-
-**J. Goldsmith**, C. M. Crainiceanu, B. S. Caffo, D. S. Reich (2012).
-Longitudinal Penalized Functional Regression for Cognitive Outcomes on Neuronal Tract Measurements.
-<i> Journal of the Royal Statistical Society: Series C, </i>
-<b>61</b> 453-469.
-[[Link](http://onlinelibrary.wiley.com/doi/10.1111/j.1467-9876.2011.01031.x/abstract) |
-[PubMed](http://www.ncbi.nlm.nih.gov/pubmed/22679339) |
-[Simulation Code](Downloads/LPFR_Code.zip)]
-
-T. Shinohara, **J. Goldsmith**, F. Mateen, D. S. Reich, C. M. Crainiceanu (2012).
-Predicting Breakdown of the Blood-Brain Barrier in Multiple Sclerosis Without Contrast Agents.
-<i> American Journal of Neuroradiology, </i>
-<b>33</b> 1586-1590.
-[[Link](http://www.ajnr.org/content/33/8/1586.long) |
-[PubMed](http://www.ncbi.nlm.nih.gov/pubmed/22442041)]
-
-J. Bai, **J. Goldsmith**, B. S. Caffo, T. Glass, C. M. Crainiceanu (2012).
-Movelets: A Dictionary of Movement.
-<i> Electronic Journal of Statistics, </i>
-<b>6</b> 559-578.
-[[Link](https://projecteuclid.org/euclid.ejs/1334065322) |
-[PubMed](http://www.ncbi.nlm.nih.gov/pubmed/23293708)]
-
-N. Louissant, S. Nimmagadda, R. Bakshi, Y. Du, K. Macura, K. King, R. Wahl, **J. Goldsmith**, B. S. Caffo,
-Y.-J. Cao, J. Anderson, E. Fuchs, C. W. Hendrix (2012).
-Distribution of Cell-free and Cell-associated HIV Surrogates in the Female Genital Tract following Simulated Vaginal Intercourse.
-<i> Journal of Infectious Diseases, </i>
-<b>205</b> 725-732.
-[[Link](http://jid.oxfordjournals.org/content/205/5/725) |
-[PubMed](http://www.ncbi.nlm.nih.gov/pubmed/22279121)]
-
-N. Louissant, S. Nimmagadda, E. Fuchs, R. Bakshi, Y. Cao, L. Lee, **J. Goldsmith**, B. S. Caffo, Y. Du, K. King,
-F. Menendez, M. Torbenson, C. W. Hendrix (2012).
-Distribution of Cell-free and Cell-associated HIV Surrogates in the Colon following Simulated Receptive Anal Intercourse.
-<i> Journal of Acquired Immune Deficiency Syndromes, Basic and Translational Science, </i>
-<b>59</b> 10-17.
-[[Link](http://ovidsp.tx.ovid.com/sp-3.12.0b/ovidweb.cgi?&S=KOLDFPPIPMDDFJDMNCMKNBLBBJIDAA00&Link+Set=S.sh.27.28.32.42%7c2%7csl_10) |
-[PubMed](http://www.ncbi.nlm.nih.gov/pubmed/21937920)]
-
-## 2011 and before
-
-**J. Goldsmith**, J. Bobb, C. M. Crainiceanu, B. S. Caffo, D. S. Reich (2011).
-Penalized Functional Regression.
-<i> Journal of Computational and Graphical Statistics, </i>
-<b>20</b> 830-851.
-[[Link](http://www.tandfonline.com/doi/abs/10.1198/jcgs.2010.10007#.U1BzC16ft94) |
-[PubMed](http://www.ncbi.nlm.nih.gov/pubmed/22368438) |
-[Simulation Code](Downloads/PFR_Code.zip)]
-
-**J. Goldsmith**, C. M. Crainiceanu, B. S. Caffo, D. S. Reich (2011).
-Penalized Functional Regression Analysis of White-Matter Tract Profiles in Multiple Sclerosis.
-<i> NeuroImage, </i>
-<b>57</b> 431-439.
-[[Link](http://www.sciencedirect.com/science/article/pii/S1053811911004435) |
-[PubMed](http://www.ncbi.nlm.nih.gov/pubmed/21554962)]
-
-**J. Goldsmith**, B. S. Caffo, C. M. Crainiceanu, D. Reich, Y. Du, C. W. Hendrix (2011).
-Nonlinear Tube-Fitting for the Analysis of Anatomical and Functional Structures.
-<i> Annals of Applied Statistics, </i>
-<b>5</b> 337-363.
-[[Link](http://projecteuclid.org/euclid.aoas/1300715193) |
-[PubMed](http://www.ncbi.nlm.nih.gov/pubmed/21709824)]
-
-**J. Goldsmith**, M. P. Wand, and C. M. Crainiceanu (2011).
-Functional Regression via Variational Bayes.
-<i> Electronic Journal of Statistics, </i>
-<b>5</b> 572-602.
-[[Link](http://projecteuclid.org/euclid.ejs/1308143123) |
-[PubMed](http://www.ncbi.nlm.nih.gov/pubmed/22163061) |
-[Simulation Code](Downloads/VB_Code.zip)]
-
-C. M. Crainiceanu, **J. Goldsmith** (2010).
-Bayesian Functional Data Analysis using WinBUGS.
-<i> Journal of Statistical Software, </i>
-<b>32</b> 1-33.
-[[Link](http://www.jstatsoft.org/v32/i11/) |
-[PubMed](http://www.ncbi.nlm.nih.gov/pubmed/21743798)]
-
-**J. Goldsmith**, L. Koss (2009).
-Dynamical Properties of the Derivative of the Weierstrass Elliptic Function.
-<i> Involve, </i>
-<b>2</b> 267-288.
-[[Link](http://msp.org/involve/2009/2-3/p02.xhtml) |
-[pdf](Downloads/Weierstrass.pdf)]
+(text placeholder)

### 2017-04-05 software.Rmd
new website; mostly complete with some chunks missing.

---
---

<link rel="stylesheet" href="styles.css" type="text/css" />

<br>

## refund

I'm lead author of the `refund` package ([CRAN](https://cran.r-project.org/web/packages/refund/index.html); [GitHub](https://github.com/refunders/refund)). I've made contributions to several functions in this package:

* `pfr()` for penalized scalar-on-function regression
* `fpca.sc()` for functional principal components analysis
* `ccb.fpc()` for improved inference for functional principal components analysis
* `bayes_fosr()` for Bayesian function-on-scalar regression

## refund.shiny

I worked with Julia Wrobel on the `refund.shiny` package ([CRAN](https://cran.r-project.org/web/packages/refund.shiny/index.html); [GitHub](https://github.com/refunders/refund.shiny); [paper](http://onlinelibrary.wiley.com/doi/10.1002/sta4.109/abstract)).

Through the `plot_shiny()` function, this package produces interactive graphics for several of the most common functional data analyses:

* Functional principal components analysis
* Multilevel and time-varying functional principal components analysis
* Function-on-scalar regression
* Functional linear concurrent regression

This package is closely aligned with the `refund` package: analyses are conducted using functions in `refund` and return objects that can be plotted using `refund.shiny::plot_shiny()`.

## GitHub packages

Code for several projects are developed on [GitHub](https://github.com/jeff-goldsmith):

* This website
* [`vbvs.concurrent`](https://github.com/jeff-goldsmith/vbvs.concurrent), a package for fitting the functional linear concurrent regression model
* [`gfpca`](https://github.com/jeff-goldsmith/gfpca), a package for generalized functional principal components analysis
* [Materials](https://github.com/jeff-goldsmith/gfpca) for a short course on variable selection in functional regression models

### 2017-04-05 teaching.Rmd
new website; mostly complete with some chunks missing.

---
---

<link rel="stylesheet" href="styles.css" type="text/css" />

<br>

## Current courses

Fall 2017: Data Science I

## Past courses

Spring 2016: Linear Regression Models  
Spring 2015: Linear Regression Models  
Summer 2015: Applied Regression II  
Spring 2014: Linear Regression Models  
Spring 2014: Categorical Data Analysis  
Spring 2013: Linear Regression Models  
Spring 2013: Categorical Data Analysis

## Short courses

2017: ["Variable Selection Methods in Functional Regression"](https://jeff-goldsmith.github.io/IWAFDA/) (at the International Workshop on Advances in Functional Data Analysis)  
2014: "Functional Data Analysis: Techniques and Applications" (at ENAR)

### 2017-04-07 index.Rmd
typo fixes
added research page info

@@
 
-<br><img src="jeff.jpg" alt="jeff" style="width:85%; border:10px solid"><br>
+<br><img src="images/jeff.jpg" alt="jeff" style="width:85%; border:10px solid"><br>
 
-I recieved a BS in mathematics from [Dickinson College](http://www.dickinson.edu) in 2007 and a PhD in Biostatistics from [Johns Hopkins University](http://www.jhsph.edu/departments/biostatistics/) in 2012.
+I received a BS in mathematics from [Dickinson College](http://www.dickinson.edu) in 2007 and a PhD in Biostatistics from [Johns Hopkins University](http://www.jhsph.edu/departments/biostatistics/) in 2012.
 My dissertation was advised by [Ciprian Crainiceanu](http://www.biostat.jhsph.edu/~ccrainic/) and [Brian Caffo](https://sites.google.com/view/bcaffo/home), and focused on statistical methods for high-dimensional structured data.
@@
 
-Email: [jeff.goldsmith@olumbia.edu](mailto:jeff.goldsmith@columbia.edu)  
+Email: [jeff.goldsmith@columbia.edu](mailto:jeff.goldsmith@columbia.edu)  
 Phone: 212-342-4599

### 2017-04-07 research.Rmd
added research page info

@@
 ---
-title: "Jeff Goldsmith"
 ---
@@
 <link rel="stylesheet" href="styles.css" type="text/css" />
+<br>
+
+I am inspired by current scientific questions to develop general, principled methods for the analysis of challenging data sets.
+The methodological developments motivated by these studies are modern functional data analysis tools required by emerging structures and scientific problems.
+
+Below are a few images stemming from my recent work.
 
@@
 
-(text placeholder)
+I'm interested in understanding the effect of stroke on motion integrity.
+In a sequence of experiments, subjects were asked to reach toward eight targets in a two-dimensional planar motion task.
+Below we show motions made by two subjects, each of whom suffers from mild stroke affecting their dominant arm.
+
+<img src="images/motions.gif" alt="kinematics" style="width:80%; border:5px solid">
+
+Our work has studied the effect of stroke on the mean and variability of these motions; the methods have also been applied to several other contexts, including motor learing in healthy subjects.
+This [interactive graphic](https://jeff-goldsmith.shinyapps.io/MotorControl_Interactive/) shows the effect of covariates on the mean of kinematic motions.
 
@@
 
-(text placeholder)
+Accelerometry is used to collect continuous information on physical activity using unobtrusive monitors worn at all times.
+Below is data gathered for 420 children in northern Manhattan and the Bronx, collected as part of a study to understand the effects of environmental exposures on health.
+In several papers we've tried to understand the effects of subject characteristics, such as age, gender, or BMI, on activity profile, as well as to assess associations between physical activity and long-term health outcomes.
+
+This graphic shows observed accelerometer data for children in this study, separated into groups based on covariates.
+Below each data plot is the coefficient function for the covariate effect estimated in a function-on-scalar regression model.
+An [interactive version](https://jeff-goldsmith.shinyapps.io/HS_interactive/) of this graphic is also available.
+
+<img src="images/accel_covariate.jpg" alt="kinematics" style="width:80%; border:5px solid">

### 2017-04-08 teaching.Rmd
added link from teaching page to linear regression site

@@
 
-Spring 2016: Linear Regression Models  
+Spring 2016: [Linear Regression Models](http://jeffgoldsmith.com/P8111/)  
 Spring 2015: Linear Regression Models  
@@
 
-2017: ["Variable Selection Methods in Functional Regression"](https://jeff-goldsmith.github.io/IWAFDA/) (at the International Workshop on Advances in Functional Data Analysis)  
+2017: ["Variable Selection Methods in Functional Regression"](http://jeffgoldsmith.com/IWAFDA/) (at the International Workshop on Advances in Functional Data Analysis)  
 2014: "Functional Data Analysis: Techniques and Applications" (at ENAR)

### 2017-04-10 best_pubs.Rmd
adding "best pubs" page
content for "best pubs" page

--- 2017-04-05 research.Rmd
@@
 <link rel="stylesheet" href="styles.css" type="text/css" />
+<br>
 
-## Motion kinematics
+Below is a collection of papers that best represents my work in statistical methods development and transdisciplinary research.
+For each, there is a brief synopsis and a link to download a PDF of the paper.
+A comprehensive list of all my publications is [here](papers.html).
 
-(text placeholder)
+#### Generalized Multilevel Function-on-Scalar Regression and Principal Component Analysis
 
-## Wearable devices
+In the study that motivates this paper, participants wore an accelerometer to record physical activity data continuously for five days.
+I treat these data as exponential-family response curves, and develop methods for function-on-scalar regression and functional principal components analysis.
 
-(text placeholder)
+[[pdf](BestPubs/MotorLearning.pdf)]
+
+#### Variable Selection in the Functional Linear Concurrent Model
+
+This paper is also motivated by wearable device data.
+Participants wore an ambulatory blood pressure monitor that recorded observations roughy every half-hour over the course of one day.
+Accompanying each measurement are survey responses regarding mood, location, behavior, activity, and other variables.
+I posed a functional linear concurrent model for these data, and developed variable selection techniques to estimate model parameters.
+
+[[pdf](BestPubs/VBVS.pdf)]
+
+#### Assessing Systematic Effects of Stroke on Motor Control using Hierarchical Function-on-Scalar Regression
+
+Stroke patients were asked to make repeated reaches toward eight targets in a two-dimensional planar motion task, and their fingertip position was recorded during the execution of each reach.
+For these data I developed a Bayesian heirarchical function-on-scalar regression model, implemented a variational approximation for fast model building, and used posterior sampling for inference.
+
+[[pdf](BestPubs/BayesPFSR.pdf)]
+
+#### Modeling motor learning using heteroskedastic functional principal components analysis
+
+A related experiment used kinematic data to quantify motor learning in healthy subjects.
+Working with a student, I proposed a novel extension of functional principal components analysis in which score variances depend on covariates and subject random effects.
+A second revision of this paper will be submitted to the _Journal of the American Statistical Association_ in the coming weeks.
+
+[[pdf](BestPubs/MotorLearning.pdf)]
+
+#### Corrected Confidence Bands for Functional Data Using Principal Components
+
+This paper addresses an issue for inference in functional principal components analysis.
+Briefly, usual approaches to inference treat estimated principal components as fixed; I demonstrated that the variability in these estimates can substantially affect the coverage of confidence bands derived as if the principal components were known.
+I also propose a bootstrap-based procedure for obtaining bands with nominal coverage.
+
+[[pdf](BestPubs/FPCA_Bands.pdf)]
+
+#### New Insights into Activity Patterns in Children, Found Using Functional Data Analyses
+
+I develop statistical methods in response to challenges in real data, and work to disseminate those methods to a broad community.
+In this paper, I described function-on-scalar regression for researchers in physical activity measurement and quantification, and apply this approach to a study of activity patterns in childrean.
+The paper was accompanied by robust, user-friendly software, and was published in the leader subject-area journal.
+
+[[pdf](BestPubs/HeadStart.pdf)]

### 2017-04-10 best_pubs.Rmd
added complete citations

@@
 A comprehensive list of all my publications is [here](papers.html).
+<br><br>
 
@@
 
-[[pdf](BestPubs/MotorLearning.pdf)]
+**J. Goldsmith**, V. Zipunnikov, J. Schrack (2015).
+Generalized Multilevel Functional-on-Scalar Regression and Principal Component Analysis.
+<i> Biometrics, </i>
+<b>71</b> 344-353.
+[[pdf](BestPubs/GenMFPCA.pdf)].
 
@@
 
-[[pdf](BestPubs/VBVS.pdf)]
+**J. Goldsmith**, J. E. Schwartz.
+Variable Selection in the Functional Linear Concurrent Model (2017+).
+<i> Statistics in Medicine, </i>
+accepted.
+[[pdf](BestPubs/VBVS.pdf)].
 
@@
 
-[[pdf](BestPubs/BayesPFSR.pdf)]
+**J. Goldsmith**, T. Kitago (2016).
+Assessing Systematic Effects of Stroke on Motor Control using Hierarchical Function-on-Scalar Regression.
+<i> Journal of the Royal Statistical Society: Series C, </i>
+<b>65</b> 215-236.
+[[pdf](BestPubs/BayesPFSR.pdf)].
 
@@
 Working with a student, I proposed a novel extension of functional principal components analysis in which score variances depend on covariates and subject random effects.
-A second revision of this paper will be submitted to the _Journal of the American Statistical Association_ in the coming weeks.
+A second revision of this paper will be submitted in the coming weeks.
 
-[[pdf](BestPubs/MotorLearning.pdf)]
+D. Backenroth, **J. Goldsmith**, M. D. Harran, J. C. Cortes, J. W. Krakauer, and T. Kitago.
+Modeling motor learning using heteroskedastic functional principal components analysis.
+<i> Journal of the American Statistical Association, </i> acceptable after major revisions.
+[[pdf](BestPubs/MotorLearning.pdf)].
 
@@
 
-[[pdf](BestPubs/FPCA_Bands.pdf)]
+**J. Goldsmith**, S. Greven, C. M. Crainiceanu (2013).
+Corrected Confidence Bands for Functional Data Using Principal Components.
+<i> Biometrics, </i>
+<b>69</b> 41-51.
+[[pdf](BestPubs/FPCA_Bands.pdf)].
 
@@
 
-[[pdf](BestPubs/HeadStart.pdf)]
+**J. Goldsmith**, X. Liu, J. S. Jacobson, A. Rundle (2016).
+New insights into activity patterns in children, found using functional data analyses.
+<i> Medicine and Science in Sports and Exercise, </i>
+<b>48</b> 1723-1729.
+[[pdf](BestPubs/HeadStart.pdf)].

### 2017-04-11 best_pubs.Rmd
only 5 papers...

@@
 Below is a collection of papers that best represents my work in statistical methods development and transdisciplinary research.
-For each, there is a brief synopsis and a link to download a PDF of the paper.
+For each, there is a brief synopsis, a full citation, and a link to download a PDF of the paper.
+
 A comprehensive list of all my publications is [here](papers.html).
@@
 [[pdf](BestPubs/GenMFPCA.pdf)].
-
+<br><br>
+<!--
 #### Variable Selection in the Functional Linear Concurrent Model
@@
 [[pdf](BestPubs/VBVS.pdf)].
+<br><br>
+-->
 
@@
 [[pdf](BestPubs/BayesPFSR.pdf)].
+<br><br>
 
@@
 [[pdf](BestPubs/MotorLearning.pdf)].
+<br><br>
 
@@
 [[pdf](BestPubs/FPCA_Bands.pdf)].
+<br><br>
 

### 2017-04-20 git.Rmd
adding a page for a git example to be used in computing club

---
---

<link rel="stylesheet" href="styles.css" type="text/css" />
<br>

This page has some stuff about Git / GitHub / GitHub with R, and is the basis for a computing club meeting.

People will get the most out of that meeting if they've installed relevant software (git, RStudio, a git client) and created a GitHub account before showing up. Instructions for doing all that can be found in Chapters 4-9 of [this book](http://happygitwithr.com) (note -- all the rest of those chapters are also awesome).

## Some slides

After going through these slides we'll shift to an interactive demostration.

## Other materials

There's a lot of stuff to help with git in general, and with git for R in particular. This is a non-exhaustive list:

* Jenny Bryan's [book](http://happygitwithr.com) (same as the link above)
* The [GitHub](https://guides.github.com/activities/hello-world/) guide
* Version control with [RStudio](https://support.rstudio.com/hc/en-us/articles/200532077-Version-Control-with-Git-and-SVN)

### 2017-04-20 git.Rmd
embedded slides for content

@@
 
+<script async class="speakerdeck-embed" data-id="b1f65532f0644b8fb5301f8fd6934b01" data-ratio="1.33333333333333" src="//speakerdeck.com/assets/embed.js"></script>
+<div style="margin-bottom:5px"> <strong> <a href="https://speakerdeck.com/jeffgoldsmith/git-slides" title="Git stuff" target="_blank">Git stuff</a> </strong> from <strong><a href="https://speakerdeck.com/jeffgoldsmith" target="_blank">Jeff Goldsmith</a></strong>.
+</div>
+
 After going through these slides we'll shift to an interactive demostration.

### 2017-08-08 papers.Rmd
fixing incorrect link for paper
updated papers list — citation for sofr review paper

@@
 
+A. L. Wong, **J. Goldsmith**, A. D. Forrence, A. M. Haith, and J. W. Krakauer (2017+).
+Habitual selection of reaction times.
+<i> eLife, </i> 
+accepted.
+
+K. M. Diaz, D. J. Krupka, M. J. Chang, I. M. Kronish, N. Moise, **J. Goldsmith**, and J. E. Schwartz (2017+).
+	Wrist-based cut-points for moderate- and vigorous-intensity physical activity for the Actical accelerometer in adults.
+<i> Journal of Sports Sciences, </i>
+accepted.
+
 J. C. Cortes<sup>&#8224;</sup>, **J. Goldsmith**<sup>&#8224;</sup>, M. Harran, J. Xu, N. Kim, A. R. Luft, P. Celnik, J. W. Krakauer, and T. Kitago (2017+).
@@
 
-P. T. Reiss, **J. Goldsmith**, H. L. Shang, R. T. Ogden.
-Methods for Scalar-on-Function Regression (2017+).
-<i> International Statistical Review, </i>
-accepted.
-
-**J. Goldsmith**, J. E. Schwartz.
+**J. Goldsmith** and J. E. Schwartz.
 Variable Selection in the Functional Linear Concurrent Model (2017+).
@@
 
-J. Gertheiss, **J. Goldsmith**, H. L. Shang, A.-M. Staicu (2017).
+P. T. Reiss, **J. Goldsmith**, H. L. Shang, and R. T. Ogden.
+Methods for Scalar-on-Function Regression (2017+).
+<i> International Statistical Review, </i>
+<b>85</b> 228-249.
+
+J. Gertheiss, **J. Goldsmith**, and A.-M. Staicu (2017).
 A note on modeling sparse exponential-family functional response curves.
@@
 
-A. Castano, M. Haq, D. Narotsky, **J. Goldsmith**, R. L. Weinberg, R. Morgenstern, T. Pozniakoff, F. L. Ruberg, E. J. Miller, J. L. Berk, A. Dispenzieri, M. Grogan, G.
+A.
+Castano, M.
+Haq, D.
+Narotsky, **J.
+Goldsmith**, R.
+L.
+Weinberg, R.
+Morgenstern, T.
+Pozniakoff, F.
+L.
+Ruberg, E.
+J.
+Miller, J.
+L.
+Berk, A.
+Dispenzieri, M.
+Grogan, G.
+Johnson, S.
+Bokhari, and M.
+S.
+Maurer (2016).
 Multicenter Experience of Planar Technetium Pyrophosphate Cardiac Imaging: Does Preferential Cardiac Uptake Predict Survival in Patients with ATTR Cardiac Amyloidosis?
@@
 <b>32</b> 5222-5240.
-[[Link](http://www.tandfonline.com/doi/abs/10.1080/10618600.2012.679241) |
-[PubMed](http://www.ncbi.nlm.nih.gov/pubmed/23794794)]
+[[Link](http://onlinelibrary.wiley.com/doi/10.1002/sim.5989/abstract) |
+[PubMed](https://www.ncbi.nlm.nih.gov/pubmed/24114808)]
 

### 2017-08-09 teaching.Rmd
placeholder for link to DSI course
links to DSI and ICAMPAM shortcourse

@@
 
-Fall 2017: Data Science I
+Fall 2017: [Data Science I](http://jeffgoldsmith.com/DSI/)
 
@@
 
+2017: ["Functional Data Analysis for Wearables: Methods and Applications"](http://jeffgoldsmith.com/ICAMPAM/) (at the International Conference on Ambulatory Monitoring of Physical Activity)  
 2017: ["Variable Selection Methods in Functional Regression"](http://jeffgoldsmith.com/IWAFDA/) (at the International Workshop on Advances in Functional Data Analysis)  

### 2017-09-05 papers.Rmd
updating papers page with a couple of recent things

@@
 ## 2017
+D. Backenroth<sup>&#8225;</sup>, **J. Goldsmith**, M. D. Harran, J. C. Cortes, J. W. Krakauer, and T. Kitago (2017+).
+Modeling motor learning using heteroskedastic functional principal components analysis.
+<i> Journal of the American Statistical Association, </i> 
+accepted.
+[[PDF](Downloads/HetFCPA.pdf)]
 
-A. L. Wong, **J. Goldsmith**, A. D. Forrence, A. M. Haith, and J. W. Krakauer (2017+).
-Habitual selection of reaction times.
-<i> eLife, </i> 
-accepted.
+M. S. Maurer, E. Horn, A. Reyentovich, V. V. Dickson, S. Pinney, D. Goldwater, N. E. Goldstein, O. Jimenez, S. Teruya, **J. Goldsmith**, S. Helmke, M. Yuzefpolskaya, and G. R Reeves (2017+).
+Can a Left Ventricular Assist Devices in Advanced Systolic Heart Failure Improve or Reverse the Frailty Phenotype?
+<i> Journal of the American Geriatrics Society, </i> accepted.
 
@@
 
+A. L. Wong, **J. Goldsmith**, A. D. Forrence, A. M. Haith, and J. W. Krakauer (2017+).
+Habitual selection of reaction times.
+<i> eLife, </i> 
+<b>6</b> e28075.
+[[Link](https://elifesciences.org/articles/28075)]
+
 P. T. Reiss, **J. Goldsmith**, H. L. Shang, and R. T. Ogden.
-Methods for Scalar-on-Function Regression (2017+).
+Methods for Scalar-on-Function Regression (2017).
 <i> International Statistical Review, </i>

### 2018-06-01 index.Rmd
typo fix
fixing links; level up

@@
 
-### Assistant Professor of Biostatistics, Columbia University Mailman School of Public Health
+### Associate Professor of Biostatistics, Columbia University Mailman School of Public Health
 
@@
 
-My full CV is availble [here](Downloads/CV_Goldsmith.pdf).
+My full CV is available [here](Downloads/CV_Goldsmith.pdf).
 

### 2018-06-02 papers.Rmd
fixing links; level up
updating papers list

@@
 
-## 2017
-D. Backenroth<sup>&#8225;</sup>, **J. Goldsmith**, M. D. Harran, J. C. Cortes, J. W. Krakauer, and T. Kitago (2017+).
+## 2018
+
+D. Backenroth<sup>&#8225;</sup>, **J. Goldsmith**, M. D. Harran, J. C. Cortes, J. W. Krakauer, and T. Kitago (2018+).
 Modeling motor learning using heteroskedastic functional principal components analysis.
@@
 
-M. S. Maurer, E. Horn, A. Reyentovich, V. V. Dickson, S. Pinney, D. Goldwater, N. E. Goldstein, O. Jimenez, S. Teruya, **J. Goldsmith**, S. Helmke, M. Yuzefpolskaya, and G. R Reeves (2017+).
-Can a Left Ventricular Assist Devices in Advanced Systolic Heart Failure Improve or Reverse the Frailty Phenotype?
-<i> Journal of the American Geriatrics Society, </i> accepted.
+H. Rosenblum, A. Castano, J. Alvarez, **J. Goldsmith**, S. Helmke, M.S. Maurer (2018).
+TTR (Transthyretin) Stabilizers Are Associated With Improved Survival in Patients With TTR Cardiac Amyloidosis.
+<i> Circulation: Heart Failure, </i>
+<b>11</b> e004769.
+[[Link](http://circheartfailure.ahajournals.org/content/11/4/e004769)
+| [PubMed](https://www.ncbi.nlm.nih.gov/pubmed/29615436)]
 
-K. M. Diaz, D. J. Krupka, M. J. Chang, I. M. Kronish, N. Moise, **J. Goldsmith**, and J. E. Schwartz (2017+).
+K. M. Diaz, D. J. Krupka, M. J. Chang, I. M. Kronish, N. Moise, **J. Goldsmith**, and J. E. Schwartz (2018).
 Wrist-based cut-points for moderate- and vigorous-intensity physical activity for the Actical accelerometer in adults.
 <i> Journal of Sports Sciences, </i>
-accepted.
+<b>36</b> 206-212.
+[[Link](https://shapeamerica.tandfonline.com/doi/abs/10.1080/02640414.2017.1293279)
+| [PubMed](https://www.ncbi.nlm.nih.gov/pubmed/28282744)]
 
-J. C. Cortes<sup>&#8224;</sup>, **J. Goldsmith**<sup>&#8224;</sup>, M. Harran, J. Xu, N. Kim, A. R. Luft, P. Celnik, J. W. Krakauer, and T. Kitago (2017+).
+## 2017
+
+K.
+M.
+Diaz, **J.
+Goldsmith**, H.
+Greenlee, G.
+Strizich, Q.
+Qi, Y.
+Mossavar-Rahmani, D.
+C.
+Vidot, C.
+Buelna, C.
+E.
+Brintz, T.
+Elfassy, L.
+C.
+Gallo, M.
+L.
+Daviglus, D.
+Sotres-Alvarez, R.
+C.
+Kaplan (2017).
+Prolonged, Uninterrupted Sedentary Behavior and Glycemic Biomarkers Among US Hispanic/Latino Adults
+<i> Circulation, </i> 
+<b>136</b> 1362-1373.
+[[Link](http://circ.ahajournals.org/content/136/15/1362)
+| [PubMed](https://www.ncbi.nlm.nih.gov/pubmed/28835368)]
+
+M. S. Maurer, E. Horn, A. Reyentovich, V. V. Dickson, S. Pinney, D. Goldwater, N. E. Goldstein, O. Jimenez, S. Teruya, **J. Goldsmith**, S. Helmke, M. Yuzefpolskaya, and G. R Reeves (2017).
+Can a Left Ventricular Assist Devices in Advanced Systolic Heart Failure Improve or Reverse the Frailty Phenotype?
+<i> Journal of the American Geriatrics Society, </i> 
+<b>65</b> 2383-2390.
+[[Link](https://onlinelibrary.wiley.com/doi/full/10.1111/jgs.15124)
+| [PubMed](https://www.ncbi.nlm.nih.gov/pubmed/28940248)]
+
+J. C. Cortes<sup>&#8224;</sup>, **J. Goldsmith**<sup>&#8224;</sup>, M. Harran, J. Xu, N. Kim, A. R. Luft, P. Celnik, J. W. Krakauer, and T. Kitago (2017).
 A short and distinct time window for recovery of arm motor control after stroke revealed with a global measure of trajectory kinematics.
 <i> Neurorehabilitation and Neural Repair, </i>
-accepted.
+<b>31</b> 552-560.
+[[Link](http://journals.sagepub.com/doi/abs/10.1177/1545968317697034)
+| [PubMed](https://www.ncbi.nlm.nih.gov/pubmed/28506149)]
 
 M. Kronish, K. M. Diaz, **J. Goldsmith**, N. Moise, and J. E. Schwartz.
-Objectively measured adherence to physical activity guidelines after acute coronary syndrome (2017+).
+Objectively measured adherence to physical activity guidelines after acute coronary syndrome (2017).
 <i> Journal of the American College of Cardiology, </i>
-accepted.
+<b>69</b> 1205.
+[[Link](https://www.sciencedirect.com/science/article/pii/S0735109717300372?via%3Dihub)
+| [PubMed](https://www.ncbi.nlm.nih.gov/pubmed/28254185)]
 
 **J. Goldsmith** and J. E. Schwartz.
-Variable Selection in the Functional Linear Concurrent Model (2017+).
+Variable Selection in the Functional Linear Concurrent Model (2017).
 <i> Statistics in Medicine, </i>
-accepted.
-[[PDF](Downloads/VBVS.pdf)
+<b>36</b> 2237-2250.
+[[Link](http://onlinelibrary.wiley.com/doi/10.1002/sim.7254/full)
+| [PubMed](https://www.ncbi.nlm.nih.gov/pubmed/28211085)
 | [GitHub](https://github.com/jeff-goldsmith/vbvs.concurrent)]
 
-A. L. Wong, **J. Goldsmith**, A. D. Forrence, A. M. Haith, and J. W. Krakauer (2017+).
+A. L. Wong, **J. Goldsmith**, A. D. Forrence, A. M. Haith, and J. W. Krakauer (2017).
 Habitual selection of reaction times.
@@
 A motor planning stage represents the shape of upcoming movement trajectories.
-<i> Journal of Neurophysiolog, </i>
+<i> Journal of Neurophysiology, </i>
 <b>116</b> 296-305.

### 2018-06-03 index.Rmd
minor updates

--- 2017-04-07 index.Rmd
@@
 <link rel="stylesheet" href="styles.css" type="text/css">
+<link rel="stylesheet" href="academicons/css/academicons.min.css"/>
 
-### Assistant Professor of Biostatistics, Columbia University Mailman School of Public Health
+Associate Professor of Biostatistics <br>
+Columbia University Mailman School of Public Health
 
-<br><img src="images/jeff.jpg" alt="jeff" style="width:85%; border:10px solid"><br>
+<br><img src="images/jeff.jpg" alt="jeff" style="width:65%; border:10px solid"><br>
+
+#### About
 
@@
 
-#### Curriculum Vitae
-
-My full CV is availble [here](Downloads/CV_Goldsmith.pdf).
-
-<br>
-
 #### Contact Information

### 2018-06-09 software.Rmd
typo fixes
updating subpage stylesheets so academicons work throughout

@@
 <link rel="stylesheet" href="styles.css" type="text/css" />
+<link rel="stylesheet" href="academicons/css/academicons.min.css"/>
 
@@
 
-## refund
+## `refund`
 
@@
 
-## refund.shiny
+## `refund.shiny`
 
@@
 
-Code for several projects are developed on [GitHub](https://github.com/jeff-goldsmith):
+Code for several projects has been developed on [GitHub](https://github.com/jeff-goldsmith):
 

### 2018-07-06 index.Rmd
replace icon; other minor rebuild updates

@@
 <link rel="stylesheet" href="academicons/css/academicons.min.css"/>
+<link rel="apple-touch-icon" href="/images/JG_transparent.png" >
 

### 2018-07-23 index.Rmd
update papers; new teaching list; change office number

@@
 [Columbia Mailman School of Public Health](http://www.mailman.columbia.edu/)  
-722 West 168th Street, Room 630  
+722 West 168th Street, Room 617  
 New York, New York 10032

### 2018-07-23 papers.Rmd
updating subpage stylesheets so academicons work throughout
update papers list and CV
update papers; new teaching list; change office number

@@
 ## 2018
+
+J. A. Woo Baidal, K. Morel, K. Nichols, E. Elbel, N. Charles, **J. Goldsmith**, L. Chen, and E. M. Taveras (2018+). 
+Sugar-sweetened beverage attitudes and consumption during the first 1,000 days of life. 
+<i> American Journal of Public Health, </i> 
+accepted.
+
+J. Wrobel<sup>&#8225;</sup>, V. Zipunnikov, J. Schrack, and **J. Goldsmith** (2018+).
+Registration for exponential family functional data.
+<i> Biometrics, </i> 
+accepted.
+
+Y. Chen<sup>&#8225;</sup>, **J. Goldsmith**, and R. T. Ogden (2018+).
+Functional data analysis of dynamic PET data.
+<i> Journal of the American Statistical Association, </i> 
+accepted.
+
+Y. Chen<sup>&#8225;</sup>, **J. Goldsmith**, and R. T. Ogden (2018+).
+Nonlinear mixed-effects models for PET data.
+<i> Transactions on Biomedical Engineering, </i> 
+accepted.
 

### 2018-07-23 teaching.Rmd
updating subpage stylesheets so academicons work throughout
update papers; new teaching list; change office number

@@
 
-Fall 2017: [Data Science I](http://jeffgoldsmith.com/DSI/)
+Fall 2018: [Data Science I](http://p8105.com)
 
@@
 
+Fall 2017: Data Science I
 Spring 2016: [Linear Regression Models](http://jeffgoldsmith.com/P8111/)  

### 2018-10-22 papers.Rmd
small update to check github ...

@@
 accepted.
+[[Link](https://ieeexplore.ieee.org/document/8424003/)]
 
@@
 <b>85</b> 228-249.
+[[Link](https://onlinelibrary.wiley.com/doi/abs/10.1111/insr.12163)
+| [PubMed](https://www.ncbi.nlm.nih.gov/pubmed/28919663)]
 
@@
 [[Link](http://jn.physiology.org/content/early/2015/07/10/jn.00336.2015.abstract)
-| [PubMed](http://www.ncbi.nlm.nih.gov/pubmed/26032276)]
+| [PubMed](https://www.ncbi.nlm.nih.gov/pubmed/26180120)]
 (&#8224; denotes equal contribution)

### 2019-03-05 papers.Rmd
add a paper
update directory name ("Downloads" -> "resources")

@@
 ## 2018
+
+J. Lee<sup>&#8225;</sup>, G. Li, W. F. Christensen, G. Collins, M. Seeley, A. E. Bowden, D. T. Fullwood, and **J. Goldsmith** (2018+). 
+Functional Data Analyses of Gait Data Measured Using In-Shoe Sensors. 
+<i> Statistics in Biosciences, </i> 
+accepted.
 
@@
 accepted.
-[[PDF](Downloads/HetFCPA.pdf)]
+[[PDF](resources/HetFCPA.pdf)]
 
@@
 [[Link](http://journals.lww.com/acsm-msse/Abstract/2016/09000/New_Insights_into_Activity_Patterns_in_Children,.11.aspx)
-| [PDF](Downloads/HeadStart.pdf)
-| [Code](Downloads/HeadStartCode.zip)
+| [PDF](resources/HeadStart.pdf)
+| [Code](resources/HeadStartCode.zip)
 | [PubMed](http://www.ncbi.nlm.nih.gov/pubmed/27183122)]
@@
 [[Link](http://onlinelibrary.wiley.com/doi/10.1002/sta4.106/abstract)
-| [PDF](Downloads/FoS_VarSelect.pdf)
+| [PDF](resources/FoS_VarSelect.pdf)
 | Implemented in [refund](https://github.com/refunders/refund) as fosr.vs()]
@@
 <b>65</b> 215-236.
-[[PDF](Downloads/BayesPFSR_Paper.pdf)
+[[PDF](resources/BayesPFSR_Paper.pdf)
 | [Link](http://onlinelibrary.wiley.com/doi/10.1111/rssc.12115/abstract)
-| [Code](Downloads/BayesPFSR_Code.zip)
+| [Code](resources/BayesPFSR_Code.zip)
 | [Shiny App](https://jeff-goldsmith.shinyapps.io/MotorControl_Interactive)]
@@
 | [PubMed](http://www.ncbi.nlm.nih.gov/pubmed/25620473)
-| [Code](Downloads/GenMFPCA_Code.zip)
+| [Code](resources/GenMFPCA_Code.zip)
 | [Shiny App](https://jeff-goldsmith.shinyapps.io/GFPCA_interactive)]
@@
 [[Link](http://www.sciencedirect.com/science/article/pii/S0167947313003629) |
-[PDF](Downloads/Ensembling_Paper.pdf) |
-[Code](Downloads/Ensembling_Code.zip)]
+[PDF](resources/Ensembling_Paper.pdf) |
+[Code](resources/Ensembling_Code.zip)]
 
@@
 [PubMed](http://www.ncbi.nlm.nih.gov/pubmed/22679339) |
-[Simulation Code](Downloads/LPFR_Code.zip)]
+[Simulation Code](resources/LPFR_Code.zip)]
 
@@
 [PubMed](http://www.ncbi.nlm.nih.gov/pubmed/22368438) |
-[Simulation Code](Downloads/PFR_Code.zip)]
+[Simulation Code](resources/PFR_Code.zip)]
 
@@
 [PubMed](http://www.ncbi.nlm.nih.gov/pubmed/22163061) |
-[Simulation Code](Downloads/VB_Code.zip)]
+[Simulation Code](resources/VB_Code.zip)]
 
@@
 [[Link](http://msp.org/involve/2009/2-3/p02.xhtml) |
-[pdf](Downloads/Weierstrass.pdf)]
+[pdf](resources/Weierstrass.pdf)]

### 2019-05-13 papers.Rmd
CV update (may 2019)

@@
 
+## 2019
+
+E. A. Gibson, **J. Goldsmith**, and M.-A. Kioumourtzoglou (2019+).
+Complex Mixtures, Complex Analyses: an Emphasis on Interpretable Results.
+<i> Current Environmental Health Reports, </i> 
+accepted.
+[[Link](https://link.springer.com/article/10.1007%2Fs40572-019-00229-5)]
+
+J. Xu, M. Branscheidt, H. Schambra, L. Steiner, M. Widmer, J. Diedrichsen, **J. Goldsmith**, M. Lindquist, T. Kitago, A. R. Luft, J. W. Krakauer, P. A. Celnik, SMARTS Study Group (2019)
+Rethinking interhemispheric imbalance as a target for stroke neurorehabilitation.
+<i> Annals of neurology, </i> 
+<b>85</b> 502-513.
+[[Link](https://onlinelibrary.wiley.com/doi/abs/10.1002/ana.25452)
+| [PubMed](https://www.ncbi.nlm.nih.gov/pubmed/30805956)]
+
+Y. Chen<sup>&#8225;</sup>, **J. Goldsmith**, and R. T. Ogden (2019).
+Nonlinear mixed-effects models for PET data.
+<i> Transactions on Biomedical Engineering, </i> 
+<b>66</b> 881-891.
+[[Link](https://ieeexplore.ieee.org/document/8424003/)]
+
+R. Liu, R. C. Shelton, N. Eldred-Skemp, **J. Goldsmith**, and S. F. Suglia (2019)
+Early Exposure to Cumulative Social Risk and Trajectories of Body Mass Index in Childhood.
+<i> Childhood Obesity, </i> 
+<b>15</b> 48-55.
+[[Link](https://www.liebertpub.com/doi/pdf/10.1089/chi.2018.0116)
+| [PubMed](https://www.ncbi.nlm.nih.gov/pubmed/30362818)]
+
 ## 2018
 
-J. Lee<sup>&#8225;</sup>, G. Li, W. F. Christensen, G. Collins, M. Seeley, A. E. Bowden, D. T. Fullwood, and **J. Goldsmith** (2018+). 
+J. Lee<sup>&#8225;</sup>, G. Li, W. F. Christensen, G. Collins, M. Seeley, A. E. Bowden, D. T. Fullwood, and **J. Goldsmith** (2018). 
 Functional Data Analyses of Gait Data Measured Using In-Shoe Sensors. 
@@
 accepted.
-
-Y. Chen<sup>&#8225;</sup>, **J. Goldsmith**, and R. T. Ogden (2018+).
-Nonlinear mixed-effects models for PET data.
-<i> Transactions on Biomedical Engineering, </i> 
-accepted.
-[[Link](https://ieeexplore.ieee.org/document/8424003/)]
 

### 2019-06-09 software.Rmd
add tidyfun to software

@@
 * `bayes_fosr()` for Bayesian function-on-scalar regression
+
+## `tidyfun`
+
+Together with Fabian Schiepl, I am an author of the [`tidyfun`](https://fabian-s.github.io/tidyfun/) package.
+This package seeks to provide accessible and well-documented software that **makes functional data analysis in `R` easy** – specifically data wrangling and exploratory analysis.
+
+The `tidyfun` webpage includes several illustrative vignettes, and [this short overview](tidyfun.html) is a quick place to get started.
 

### 2019-06-09 tidyfun.Rmd
tidyfun example! mostly for a conference

---
title: "`tidyfun`"
output:
  html_document: 
    toc: true
    toc_float: true
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

library(tidyverse)

theme_set(theme_bw() + theme(legend.position = "bottom"))
```

This page hosts a presentation / quick intro to `tidyfun` -- enjoy!

## Some slides

<script async class="speakerdeck-embed" data-id="f0d309fcbf2c4d5d9d121eee4a6144ee" data-ratio="1.77777777777778" src="//speakerdeck.com/assets/embed.js"></script>
<div style="margin-bottom:5px"> <strong> <a href="https://speakerdeck.com/jeffgoldsmith/tidyfun" title="tidyfun" target="_blank">tidyfun</a> </strong> from <strong><a href="https://speakerdeck.com/jeffgoldsmith" target="_blank">Jeff Goldsmith</a></strong>. </div><br>

## Example usage

The code in this page is drawn from [`tidyfun`](https://fabian-s.github.io/tidyfun/) vignettes, and is intended as a quick introduction; for more details, please read the complete documentation!

If you haven't installed `tidyfun` the code below will do so.

```{r, eval = FALSE}
devtools::install_github("fabian-s/tidyfun")
```

Next I'll load the package, as well as the `tidyverse`.

```{r}
library(tidyfun)
library(tidyverse)
```

### Illustrative datasets

The datasets used in this vignette are the `tidyfun::chf_df` and `tidyfun::dti_df` dataset. The first contains minute-by-minute observations of log activity counts (stored as a `tfd` vector called `activity`) over seven days for each of 47 subjects with congestive heart failure. In addition to `id` and `activity`, we observe several covariates.

```{r view_chf}
data(chf_df)
```

A quick plot of these data is below.

```{r plot_chf}
chf_df %>% 
  ggplot(aes(y = activity)) + 
    geom_spaghetti(alpha = .05)
```

The `tidyfun::dti_df` contains ractional anisotropy (FA) tract profiles for the corpus callosum (cca) and the right corticospinal tract (rcst), along with several covariates.

```{r view_dti}
data(dti_df)
```

A quick plot of the `cca` tract profiles is below.

```{r plot_dti}
dti_df %>% 
  ggplot(aes(y = cca)) + 
    geom_spaghetti(alpha = .05)
```

### `tf` vectors

**`tf`** is a new data type for (vectors of) functional data:

- an abstract superclass for functional data in 2 forms:
    - as (argument, value)-tuples: subclass **`tfd`**, also irregular or sparse
    - or in basis representation: subclass **`tfb`**

- Includes additional attributes that define *function-like* behavior:
    - how to **evaluate** the given "functions" for new arguments
    - their **domain** 
    - the **resolution** of the argument values

First I'll pull a `tf` vector from the `tidyfun::dti_df` dataset, and then I'll extract a simple 5-element vector of functions interpolated to be on a regular grid. The resulting vector contain fractional anisotropy tract profiles for the corpus callosum (`cca`). When printed, `tf` vectors show the first few `arg` and `value` pairs for each subject.

```{r load-dti}
data("dti_df")

cca_five = dti_df$cca[1:5]
cca_five = tfd(cca_five, arg = seq(0, 1, l = 93), interpolate = TRUE)

cca_five
```

For illustration, we plot the vector `cca_five` below.

```{r, ex-fig}
plot(cca_five)
```

Functional data in basis representation:

- represented as a list of **`coefficients`** and a common **`basis_matrix`** of basis function evaluations on a vector of `arg`-values.
- contains a **`basis`** function that defines how to compute the basis for new **`arg`**s and how to differentiate or integrate it.
- (internal) flavors: 
    - `tfb_spline`: uses `mgcv`-spline bases 
    - `tfb_fpc`: uses functional principal components

It's possible to convert between types.

```{r}
cca_five_b = 
  cca_five %>% 
  tfb()
```

A quick plot illustrates the difference visually; lots of things are different in the background!

```{r}
plot(cca_five)
lines(cca_five_b, col = "red")
```

### Operations on `tf` vectors

The following is a brief overview of the kinds of operations available for `tf` vectors.

You can perform basic arithmetic and logical comparisons:

```{r}
cca_five[1] + cca_five[1] == 2 * cca_five[1]
log(exp(cca_five[2])) == cca_five[2]
cca_five - (2:-2) != cca_five 
```

You can summarize using `mean`, `sd`, and other functions:

```{r}
c(mean = mean(cca_five), sd = sd(cca_five))
```

You can smooth data using `tf_smooth`; this differs from converting to subclass `tfb`:

```{r}
cca_five_smooth = 
  cca_five %>% 
  tf_smooth("lowess")

plot(cca_five)
lines(cca_five_smooth, col = "blue")
```

You can determine whether a function satisfies a logical condition anywhere:

```{r}
cca_five %>% 
  tf_anywhere(value > .65)
```

And you can zoom in on regions of interest:

```{r}
cca_five_zoom = 
  cca_five %>% 
  tf_zoom(.5, 1)

plot(cca_five_zoom)
```

### `tf` vectors in dataframes

The main goal of `tidyfun` is to ease exploratory analysis by putting functional data in data frames. Since `tf` vectors are treated the same way as vectors of class `numeric` or `factor`, they can enter dataframes the same way.

The DTI data, for example, include scalar covariates and two functional variables:

```{r}
dti_df
```

And the CHF data is an example of a multilevel dataset with a functional observation:

```{r}
chf_df 
```

Now our functional data are tidy! That is, we have data rectangles, and each functional observation exists in a single "cell".

### Data wrangling

Dataframes using `tidyfun` to store functional observations can be manipulated using tools from `dplyr`, including `select` and `filter`:

```{r}
chf_df %>% 
  select(id, day, activity) %>% 
  filter(day == "Monday") %>% 
  ggplot(aes(y = activity)) + 
  geom_spaghetti(alpha = .05)
```

Operations using `group_by` and `summarize` are allowed:

```{r}
chf_df %>% 
  group_by(day) %>% 
  summarize(mean_act = mean(activity)) %>% 
  ggplot(aes(y = mean_act, color = day)) + 
  geom_spaghetti()
```

One can `mutate` functional observations -- here we exponentiate the log activity counts to obtain original recordings:

```{r}
chf_df %>% 
  mutate(exp_act = exp(activity)) %>% 
  ggplot(aes(y = exp_act)) + 
  geom_spaghetti(alpha = .05)
```

Some `dplyr` functions are most useful in conjunction with new functions in `tidyfun`. For example, one might use `filter` with `tf_anywhere` to filter based on the values of observed functions:

```{r}
chf_df %>% 
  filter(tf_anywhere(activity, value > 9)) %>% 
  ggplot(aes(y = activity)) + 
  geom_spaghetti()
```

One can add smoothed versions of existing observations using `mutate` and `tf_smooth`:

```{r}
chf_df %>% 
  filter(id == 1) %>% 
  mutate(smooth_act = tf_smooth(activity)) %>% 
  ggplot(aes(y = smooth_act)) + 
  geom_spaghetti()
```

One can also extract observations over a subset of the full domain using `mutate` and `tf_zoom`:

```{r}
chf_df %>% 
  filter(id == 1) %>% 
  mutate(daytime_act = tf_zoom(activity, 360, 1200)) %>% 
  ggplot(aes(y = daytime_act)) + 
  geom_spaghetti()
```

In general, EDA for functional data using `tidyverse` tools is now possible, and is often most powerful when paired with new functions in `tidyfun`.

### Visualization

We've seen both `plot` and `geom_spaghetti` to aid in understanding some content to this point -- base R for `tf` vectors, `ggplot` for tidy data. You can use more advanced options and combine with data wrangling steps.

You can use facetting:

```{r}
chf_df %>% 
  filter(day %in% c("Monday", "Sunday")) %>% 
  ggplot(aes(y = activity, color = gender)) + 
  geom_spaghetti(alpha = .1) + 
  facet_grid(~ day)
```

Together with data manipulation tools, the integration with `ggplot` can produce useful exploratory analyses. Note that this plot also introduces `geom_meatballs()`:

```{r}
chf_df %>% 
  group_by(gender, day) %>% 
  summarize(mean_act = mean(activity)) %>% 
  mutate(smooth_mean = tfb(mean_act)) %>% 
  filter(day %in% c("Monday", "Sunday")) %>% 
  ggplot(aes(y = smooth_mean, color = gender)) + 
  geom_spaghetti(size = 1.25, alpha = 1) + 
  geom_meatballs(aes(y = mean_act), alpha = .1) + 
  facet_grid(~ day)
```

Lasagna plots are a variant on a heatmaps which show functional observations in rows and use color to illustrate values taken at different arguments. In `tidyfun`, lasagna plots are implemented through `gglasagna`. A first example, using the CHF data, is below.

```{r}
chf_df %>% 
  filter(day %in% c("Monday", "Sunday")) %>% 
  gglasagna(activity)
```

A somewhat more involved example, demonstrating the `order` argument and taking advantage of facetting, is next.

```{r, dti-fig2}  
dti_df %>% 
  gglasagna(
    y = cca, 
    order = tf_integrate(cca, definite = TRUE), 
    arg = seq(0,1, l = 101)) + 
  theme(axis.text.y = element_text(size = 6)) + 
  facet_wrap(~ case, ncol = 2, scales = "free")
```

### Conversion

The `DTI` data in the `refund` package has been a popular example in functional data analysis. In the code below, we create a data frame (or `tibble`) containing scalar covariates, and then add columns for the `cca` and `rcst` track profiles. This code was used to create the `tidyfun::dti_df` dataset included in the package.

```{r}
dti_df = tibble(
  id = refund::DTI$ID, 
  sex = refund::DTI$sex, 
  case = factor(ifelse(refund::DTI$case, "MS", "control")))

dti_df$cca = tfd(refund::DTI$cca, arg = seq(0,1, l = 93))
dti_df$rcst = tfd(refund::DTI$rcst, arg = seq(0, 1, l = 55))
```

"Long" format data frames containing functional data include columns containing a subject identifier, the functional argument, and the value each subject's function takes at each argument. There are also often (but not always) non-functional covariates that are repeated within a subject. For data in this form, we use `tf_nest` to produce a data frame containing a single row for each subject.

An example is the pig weight data from the `SemiPar` package, which is a nice example from longitudinal data analysis. This includes columns for `id.num`, `num.weeks`, and `weight` -- which correspond to the subject, argument, and value.

```{r}
data("pig.weights", package = "SemiPar")

pig.weights = as_tibble(pig.weights)

pig.weights
```

We create `pig_df` by nesting weight within subject. The result is a data frame containing a single row for each pig, and columns for `id.num` and the `weight` function.

```{r}
pig_df = 
  pig.weights %>% 
  tf_nest(weight, .id = id.num, .arg = num.weeks)

pig_df
```

Additional functions allow conversion from other data structures to `tf` vectors, and also implement conversions back to these data structures.

## Next steps

`tidyfun` itself is a work in progress:

* There are several open issues / to dos / bug fixes
* We have some ideas for new features
* User feedback will help!

Integration with analysis is longer-term goal

* Some `refund` functions have been unofficially updated to work with dataframe / `tf` intpus
* More robust / complete integration is needed

### 2019-06-09 teaching.Rmd
add webinar info
update directory name ("Downloads" -> "resources")
typo fix, general update of infrastructure

@@
 
-Fall 2018: [Data Science I](http://p8105.com)
+Fall 2019: [Data Science I](http://p8105.com)
 
@@
 
-Fall 2017: Data Science I
+Fall 2018: [Data Science I](http://p8105.com)  
+Fall 2017: [Data Science I](http://p8105.com)  
 Spring 2016: [Linear Regression Models](http://jeffgoldsmith.com/P8111/)  
@@
 2014: "Functional Data Analysis: Techniques and Applications" (at ENAR)
+
+## Other materials
+
+2018: Webinar: ["Data Science and Predictive Models in Public Health"]() and accompanying [reproducible lasso example](resources/lasso_example.zip) (webinar requires registration of free account)

### 2019-06-09 tidyfun.Rmd
fix speakerdeck embed code in tidyfun

@@
 
-<script async class="speakerdeck-embed" data-id="f0d309fcbf2c4d5d9d121eee4a6144ee" data-ratio="1.77777777777778" src="//speakerdeck.com/assets/embed.js"></script>
+<script async class="speakerdeck-embed" data-id="1a71e0ecac2e4d7dbe07ad6d23fb6d76" data-ratio="1.77777777777778" src="//speakerdeck.com/assets/embed.js"></script>
 <div style="margin-bottom:5px"> <strong> <a href="https://speakerdeck.com/jeffgoldsmith/tidyfun" title="tidyfun" target="_blank">tidyfun</a> </strong> from <strong><a href="https://speakerdeck.com/jeffgoldsmith" target="_blank">Jeff Goldsmith</a></strong>.

### 2019-06-11 tidyfun.Rmd
some post-conference tweaks to tidyfun talk

@@
 
-This page hosts a presentation / quick intro to `tidyfun` -- enjoy!
+This page hosts a presentation / quick intro to [`tidyfun`](https://fabian-s.github.io/tidyfun/) -- enjoy!
 
@@
 
-The `tidyfun::dti_df` contains ractional anisotropy (FA) tract profiles for the corpus callosum (cca) and the right corticospinal tract (rcst), along with several covariates.
+The `tidyfun::dti_df` contains fractional anisotropy (FA) tract profiles for the corpus callosum (cca) and the right corticospinal tract (rcst), along with several covariates.
 
@@
 
-**`tf`** is a new data type for (vectors of) functional data:
+**`tf`** is a new data type for (vectors of) functional data.
+It contains subclasses for "raw" functional data (`tfd`) that can be dense / sparse and regular / irregular, and for "basis representation" functional data (`tfb`).
+Internally, there are attributes that define *function-like* behavior, including evaluation for new arguments, resolution, and the functional domain.
 
-- an abstract superclass for functional data in 2 forms:
-    - as (argument, value)-tuples: subclass **`tfd`**, also irregular or sparse
-    - or in basis representation: subclass **`tfb`**
-
-- Includes additional attributes that define *function-like* behavior:
-    - how to **evaluate** the given "functions" for new arguments
-    - their **domain** 
-    - the **resolution** of the argument values
-
-First I'll pull a `tf` vector from the `tidyfun::dti_df` dataset, and then I'll extract a simple 5-element vector of functions interpolated to be on a regular grid.
+First I'll pull a `tf` vector from the `tidyfun::dti_df` dataset.
 The resulting vector contain fractional anisotropy tract profiles for the corpus callosum (`cca`).
@@
 cca_five = dti_df$cca[1:5]
-cca_five = tfd(cca_five, arg = seq(0, 1, l = 93), interpolate = TRUE)
-
 cca_five
@@
 
-Functional data in basis representation:
-
-- represented as a list of **`coefficients`** and a common **`basis_matrix`** of basis function evaluations on a vector of `arg`-values.
-- contains a **`basis`** function that defines how to compute the basis for new **`arg`**s and how to differentiate or integrate it.
-- (internal) flavors: 
-    - `tfb_spline`: uses `mgcv`-spline bases 
-    - `tfb_fpc`: uses functional principal components
-
-It's possible to convert between types.
+Converting "raw" to "basis" representation is possible, and introduces some smoothing by default.
 
@@
 c(mean = mean(cca_five), sd = sd(cca_five))
-```
-
-You can smooth data using `tf_smooth`; this differs from converting to subclass `tfb`:
-
-```{r}
-cca_five_smooth = 
-  cca_five %>% 
-  tf_smooth("lowess")
-
-plot(cca_five)
-lines(cca_five_smooth, col = "blue")
 ```
@@
 
-Integration with analysis is longer-term goal
+Integration with analysis is longer-term goal:
 

### 2019-11-18 index.Rmd
update landing page text

@@
 
+#### Research
+
+For several years, I have worked to advance the state-of-the-art in functional data analysis by developing methods for understanding patterns in large, complex datasets in neuroscience, physical activity monitoring, and other areas.
+
+Working closely with clinicians and neuroscientists around the world, my collaborators and I have focused on improving the understanding skilled movements.
+This work involves reaching movements made by stroke patients: in these experiments, a patient's fingertip position is recorded hundreds of time per second for the duration of the reach.
+I have developed new statistical methods to understand the impact of stroke on movement quality, and applied these to large, longitudinal datasets.
+In parallel, I have proposed methods for wearable device research, especially focusing on accelerometers.
+These devices can produce minute-by-minute (or even finer) resolution observations of activity for hundreds of participants over several days, weeks, or months.
+The methods developed include approaches for regression with activity trajectories as outcomes; for interpretable dimension reduction; and for aligning major patterns (like wake from sleep, mid-day dips in activity, and sleep onset) across subjects.
+
+#### Data science
+
+Data science is a newly-formed and, as yet, loosely-defined discipline that has nonetheless emerged as a critical component of successful research in biostatistics and public health.
+For several years, I have worked to incorporate data science techniques for transparency and reproducibiity into  biostatistical analyses.
+Research projects are accompanied by robust, publicly available software and analytical pipelines that ensure the reproducibility of the results.
+This is informed by my work in developing a graduate course in [data science](https://p8105.com).
+
 #### About
@@
 I joined Columbia as an assistant professor in 2012.
-
-My statistical research is generally focused on functional data analysis, and draws heavily from ongoing collaborations with researchers in other disciplines.
-One major emphasis is the use of motion kinematics to understand motor control, skill learning, and recovery following stroke; another is physical activity measurement and quantification using wearable devices.
-The [research](research.html) page has more information on recent projects.
 

### 2019-11-18 index.Rmd
language tweaks

@@
 Data science is a newly-formed and, as yet, loosely-defined discipline that has nonetheless emerged as a critical component of successful research in biostatistics and public health.
-For several years, I have worked to incorporate data science techniques for transparency and reproducibiity into  biostatistical analyses.
+I work to incorporate data science techniques for transparency and reproducibiity into biostatistical analyses.
 Research projects are accompanied by robust, publicly available software and analytical pipelines that ensure the reproducibility of the results.
-This is informed by my work in developing a graduate course in [data science](https://p8105.com).
+This approach is informed by my work in developing a graduate course in [data science](https://p8105.com).
 

### 2019-11-25 teaching.Rmd
link to this workshop kinda thing

@@
 
+2019: [Workshop on website development](http://jeffgoldsmith.com/ehs_workshop/index.html)
 2018: Webinar: ["Data Science and Predictive Models in Public Health"]() and accompanying [reproducible lasso example](resources/lasso_example.zip) (webinar requires registration of free account)

### 2019-12-31 papers.Rmd
fix link to CV, minor updates elsewhere

@@
 [[Link](https://link.springer.com/article/10.1007%2Fs40572-019-00229-5)]
+
+E. A. Gibson, Y. Nunez, A. Abuawad, A. R. Zota, S. Renzetti, K. L. Devick, C. Gennings, **J. Goldsmith**, B. A. Coull, and M.-A. Kioumourtzoglou. (2019)
+An overview of methods to address distinct research questions on environmental mixtures: an application to persistent organic pollutants and leukocyte telomere length.
+<i> Environmental Health, </i> 
+<b>18</b> ???.
+[[Link](https://ehjournal.biomedcentral.com/articles/10.1186/s12940-019-0515-1)
+| [PubMed](https://www.ncbi.nlm.nih.gov/pubmed/31462251)
+| Article selected as NIEHS [Extramural Paper of the Month](https://factor.niehs.nih.gov/2019/11/papers/dert/index.htm)]
 

### 2019-12-31 research.Rmd
updating subpage stylesheets so academicons work throughout
fix link to CV, minor updates elsewhere

@@
 <link rel="stylesheet" href="styles.css" type="text/css" />
+<link rel="stylesheet" href="academicons/css/academicons.min.css"/>
+
 <br>
@@
 
-<img src="images/accel_covariate.jpg" alt="kinematics" style="width:80%; border:5px solid">
+<img src="images/accel_covariate.jpg" alt="accel" style="width:80%; border:5px solid">

### 2019-12-31 tidyfun.Rmd
fix link to CV, minor updates elsewhere

@@
 
-The code in this page is drawn from [`tidyfun`](https://fabian-s.github.io/tidyfun/) vignettes, and is intended as a quick introduction; for more details, please read the complete documentation!
+The code in this page is drawn from [`tidyfun`](https://tidyfun.github.io/tidyfun/) vignettes, and is intended as a quick introduction; for more details, please read the complete documentation!
 
@@
 ```{r, eval = FALSE}
-devtools::install_github("fabian-s/tidyfun")
+devtools::install_github("tidyfun/tidyfun")
 ```

### 2020-01-13 papers.Rmd
update 2020-01-13

@@
 
+## 2020
+
+D. Backenroth<sup>&#8224;</sup>, R. T. Shinohara, J. A. Schrack, and **J. Goldsmith** (2020+).
+Non-negative decomposition of functional count data. 
+<i> Biometrics, </i>  accepted.
+
+A. E. Margolis, J. Broitman, J. M. Davis, L. Alexander, A. Hamilton, Z. Liao, S. Banker, L. Thomas, G. A. Salum, K. Merikangis, **J. Goldsmith**, T. Paus, K. Keyes, M. P. Milham (2020+).
+Prevalence Of Nonverbal Learning Disability In Three Community Samples
+<i> JAMA Network Open, </i> accepted.
+
+D. Pagliaccio et al (2020+).
+Prenatal Exposure to Polycyclic Aromatic Hydrocarbons Modifies the Effects of Early Life Stress on Attention & Thought Problems in Late Childhood.
+<i> The Journal of Child Psychology and Psychiatry,, </i> accepted.
+
 ## 2019
+
+E. A. Gibson, Y. Nunez, A. Abuawad, A. R. Zota, S. Renzetti, K. L. Devick, C. Gennings, **J. Goldsmith**, B. A. Coull, and M.-A. Kioumourtzoglou. (2019)
+An overview of methods to address distinct research questions on environmental mixtures: an application to persistent organic pollutants and leukocyte telomere length.
+<i> Environmental Health, </i> 
+<b>18</b> 76.
+[[Link](https://ehjournal.biomedcentral.com/articles/10.1186/s12940-019-0515-1)
+| [PubMed](https://www.ncbi.nlm.nih.gov/pubmed/31462251)
+| Article selected as NIEHS [Extramural Paper of the Month](https://factor.niehs.nih.gov/2019/11/papers/dert/index.htm)]
+
+R. Kundert, **J. Goldsmith**, J. Veerbeek, J. W. Krakauer, and A. R. Luft (2019). 
+What the proportional recovery rule is (and is not): methodological and statistical considerations.
+<i>Neurorehabilitation and Neural Repair, </i> 
+<b>33</b> 876-887.
+[[Link](https://journals.sagepub.com/doi/full/10.1177/1545968319872996)
+| [PubMed](https://www.ncbi.nlm.nih.gov/pubmed/31524062)]
+
+A.G. Rundle, D. Gallagher, J. B. Herbstman, **J. Goldsmith**, D. Holmes, A. Hassoun, S. Oberfield, R. L. Miller, H. Andrews, E. M. Widen, L. A. Hoepner, and F. Perera (2019). 
+Prenatal Exposure to Airborne Polycyclic Aromatic Hydrocarbons and Childhood Growth Trajectories from Age 5 to 14 Years.
+<i>Environmental Research, </i> 
+<b>177</b> 108595.
+[[Link](https://www.sciencedirect.com/science/article/abs/pii/S0013935119303925)
+| [PubMed](https://www.ncbi.nlm.nih.gov/pubmed/31352299)]
+
+J. Lee<sup>&#8225;</sup>, G. Li, W. F. Christensen, G. Collins, M. Seeley, A. E. Bowden, D. T. Fullwood, and **J. Goldsmith** (2019). 
+Functional Data Analyses of Gait Data Measured Using In-Shoe Sensors. 
+<i> Statistics in Biosciences, </i> 
+<b>11</b> 288-313.
+[[Link](https://link.springer.com/article/10.1007/s12561-018-9226-3)]
 
@@
 [[Link](https://link.springer.com/article/10.1007%2Fs40572-019-00229-5)]
+| [PubMed](https://www.ncbi.nlm.nih.gov/pubmed/31069725)]
 
-E. A. Gibson, Y. Nunez, A. Abuawad, A. R. Zota, S. Renzetti, K. L. Devick, C. Gennings, **J. Goldsmith**, B. A. Coull, and M.-A. Kioumourtzoglou. (2019)
-An overview of methods to address distinct research questions on environmental mixtures: an application to persistent organic pollutants and leukocyte telomere length.
-<i> Environmental Health, </i> 
-<b>18</b> ???.
-[[Link](https://ehjournal.biomedcentral.com/articles/10.1186/s12940-019-0515-1)
-| [PubMed](https://www.ncbi.nlm.nih.gov/pubmed/31462251)
-| Article selected as NIEHS [Extramural Paper of the Month](https://factor.niehs.nih.gov/2019/11/papers/dert/index.htm)]
+Y. Chen<sup>&#8225;</sup>, **J. Goldsmith**, and R. T. Ogden (2019).
+Functional data analysis of dynamic PET data.
+<i> Journal of the American Statistical Association, </i> 
+<b>114</b> 595-609.
+[[Link](https://www.tandfonline.com/doi/abs/10.1080/01621459.2018.1497495)
+| [PubMed](https://www.ncbi.nlm.nih.gov/pubmed/31447493)]
 
@@
 
-Y. Chen<sup>&#8225;</sup>, **J. Goldsmith**, and R. T. Ogden (2019).
-Nonlinear mixed-effects models for PET data.
-<i> Transactions on Biomedical Engineering, </i> 
-<b>66</b> 881-891.
-[[Link](https://ieeexplore.ieee.org/document/8424003/)]
+J. Wrobel<sup>&#8225;</sup>, V. Zipunnikov, J. Schrack, and **J. Goldsmith** (2019).
+Registration for exponential family functional data.
+<i> Biometrics, </i> 
+<b>75</b> 48-57.
+[[Link](https://onlinelibrary.wiley.com/doi/full/10.1111/biom.12963)]
 
@@
 
+Y. Chen<sup>&#8225;</sup>, **J. Goldsmith**, and R. T. Ogden (2019).
+Nonlinear mixed-effects models for PET data.
+<i> Transactions on Biomedical Engineering, </i> 
+<b>66</b> 881-891.
+[[Link](https://ieeexplore.ieee.org/document/8424003/) 
+| [PubMed](https://www.ncbi.nlm.nih.gov/pubmed/30072311)]
+
 ## 2018
 
-J. Lee<sup>&#8225;</sup>, G. Li, W. F. Christensen, G. Collins, M. Seeley, A. E. Bowden, D. T. Fullwood, and **J. Goldsmith** (2018). 
-Functional Data Analyses of Gait Data Measured Using In-Shoe Sensors. 
-<i> Statistics in Biosciences, </i> 
-accepted.
+D. Backenroth<sup>&#8225;</sup>, **J. Goldsmith**, M. D. Harran, J. C. Cortes, J. W. Krakauer, and T. Kitago (2018).
+Modeling motor learning using heteroskedastic functional principal components analysis.
+<i> Journal of the American Statistical Association, </i> 
+<b>113</b> 1003-1015.
+[[Link](https://www.tandfonline.com/doi/abs/10.1080/01621459.2017.1379403) 
+| [PubMed](https://www.ncbi.nlm.nih.gov/pubmed/30416231)]
 
@@
 <i> American Journal of Public Health, </i> 
-accepted.
-
-J. Wrobel<sup>&#8225;</sup>, V. Zipunnikov, J. Schrack, and **J. Goldsmith** (2018+).
-Registration for exponential family functional data.
-<i> Biometrics, </i> 
-accepted.
-
-Y. Chen<sup>&#8225;</sup>, **J. Goldsmith**, and R. T. Ogden (2018+).
-Functional data analysis of dynamic PET data.
-<i> Journal of the American Statistical Association, </i> 
-accepted.
-
-D. Backenroth<sup>&#8225;</sup>, **J. Goldsmith**, M. D. Harran, J. C. Cortes, J. W. Krakauer, and T. Kitago (2018+).
-Modeling motor learning using heteroskedastic functional principal components analysis.
-<i> Journal of the American Statistical Association, </i> 
-accepted.
-[[PDF](resources/HetFCPA.pdf)]
+<b>108</b> 1659-1665.
+[[Link](https://ajph.aphapublications.org/doi/abs/10.2105/AJPH.2018.304691) 
+| [PubMed](https://www.ncbi.nlm.nih.gov/pubmed/30359102)]
 

### 2020-12-10 tidyfun.Rmd
tidyfun has been updated!!

@@
 library(tidyfun)
+library(refundr)
 library(tidyverse)
@@
   select(id, day, activity) %>% 
-  filter(day == "Monday") %>% 
+  filter(day == "Mon") %>% 
   ggplot(aes(y = activity)) + 
@@
 chf_df %>% 
-  filter(day %in% c("Monday", "Sunday")) %>% 
+  filter(day %in% c("Mon", "Sun")) %>% 
   ggplot(aes(y = activity, color = gender)) + 
   geom_spaghetti(alpha = .1) + 
-  facet_grid(~ day)
+  facet_grid(gender ~ day)
 ```
@@
   mutate(smooth_mean = tfb(mean_act)) %>% 
-  filter(day %in% c("Monday", "Sunday")) %>% 
+  filter(day %in% c("Mon", "Sun")) %>% 
   ggplot(aes(y = smooth_mean, color = gender)) + 
@@
 chf_df %>% 
-  filter(day %in% c("Monday", "Sunday")) %>% 
+  filter(day %in% c("Mon", "Sun")) %>% 
   gglasagna(activity)
@@
 
+## Some FPCA
+
+```{r}
+# irregular data 
+data(dti_df)
+dti_fpca = rfr_fpca(Y = "cca", data = dti_df)
+
+dti_df %>% 
+  modelr::add_predictions(dti_fpca, var = "cca_fits") %>% 
+  filter(case == "control") %>% 
+  ggplot(aes(y = cca_fits)) + 
+  geom_spaghetti(alpha = .4) + 
+  geom_spaghetti(aes(y = cca), color = "blue", alpha = .3) + 
+  facet_grid(~sex)
+```
+
 ## Next steps

### 2021-04-20 papers.Rmd
update papers and CV

@@
 
-D. Backenroth<sup>&#8224;</sup>, R. T. Shinohara, J. A. Schrack, and **J. Goldsmith** (2020+).
+D. Backenroth$^\ddagger$, R. T. Shinohara, J. A. Schrack, and **J Goldsmith** (2020).
 	Non-negative decomposition of functional count data. 
-<i> Biometrics, </i>  accepted.
+	<i> Biometrics, </i> 
+	<b>76</b> 1273-1284.
+	[[Link](https://onlinelibrary.wiley.com/doi/abs/10.1111/biom.13220)]
 
-A. E. Margolis, J. Broitman, J. M. Davis, L. Alexander, A. Hamilton, Z. Liao, S. Banker, L. Thomas, G. A. Salum, K. Merikangis, **J. Goldsmith**, T. Paus, K. Keyes, M. P. Milham (2020+).
+J Wrobel$^\ddagger$, ML Martin, R Bakshi, PA Calabresi, M Elliot, D Roalf, RC Gur, RE Gur, RG Henry, G Nair, J Oh, N Papinutto, D Pelletier, Daniel Salo Reich, WD Rooney, TD Satterthwaite, W Stern, K Prabhakaran, NL Sicotte, RT Shinohara, \bf J.
+Goldsmith \rm (2020).
+	Intensity warping for multisite MRI harmonization.
+	<i> NeuroImage, </i> 
+	<b>223</b> 117284.
+
+D Pagliaccio, JB Herbstman, F Perera, D Tang, J Goldsmith, BS Peterson, V Rauh, AE and Margolis (2020). 
+  Prenatal exposure to polycyclic aromatic hydrocarbons modifies the effects of early life stress on attention and Thought Problems in late childhood. 
+  <i> Journal of Child Psychology and Psychiatry, </i> 
+  <b>61</b> 1253-1265.
+
+J M Griffin, L Chiu, K M Axsom, R Bijou, K J Clerkin, P Colombo, M O Cuomo, J De Los Santos, J A Fried, **J Goldsmith**, M Habal, J Haythe, S Helmke, E M Horn, F Latif, S H Lee, E F Lin, Y Naka, J Raikhelkar, S Restaino, G T Sayer, H Takayama, K Takeda, S Teruya, V Topkara, E J Tsai, N Uriel, M Yuzefpolskaya, M A Farr, M S Maurer (2020).
+	United network for organ sharing outcomes after heart transplantation for al compared to ATTR cardiac amyloidosis	
+	<i> Annals of the American Thoracic Society, </i> 
+	<b>34</b> e14028.
+
+L R Mitrani, J De Los Santos, E Driggin, R Kogan, S Helmke, **J Goldsmith**, A B Biviano, M S Maurer (2020). 
+	Anticoagulation with warfarin compared to novel oral anticoagulants for atrial fibrillation in adults with transthyretin cardiac amyloidosis: comparison of thromboembolic events and major bleeding
+	<i> Amyloid, </i> 
+	<b>28</b> 30-34.
+
+H Rosenblum, A Masri, D L Narotsky, **J Goldsmith**, N Hamid, R T Hahn, S Kodali, T Vahl, T Nazif, O K Khalique, S Bokhari, P Soman, J L Cavalcante, M S Maurer, A Castano
+	Unveiling outcomes in coexisting severe aortic stenosis and transthyretin cardiac amyloidosis (2020).
+	<i> European Journal of Heart Failure, </i> 
+	<b>23</b> 250-258.
+
+M He, P Kinney, C Chen, Q Sun, J Ban, J Wang, S Liu,  **J Goldsmith**, M-A Kioumourtzoglou (2020).
+	Short- and intermediate- term exposure to NO2 and mortality: a multi-county analysis in China. 
+	<i> Environmental Pollution, </i> 
+	<b>261</b> 114165.
+
+E Driggin, S Helmke, J De Los Santos, S Teruya, S Guadalupe, **J Goldsmith**, M S Maurer (2020).
+	Markers of nutritional status and inflammation in transthyretin cardiac amyloidosis: association with outcomes and the clinical phenotype.
+	<i> Amyloid, </i> 
+	<b>27</b> 73-80.
+
+A. E. Margolis, J. Broitman, J. M. Davis, L. Alexander, A. Hamilton, Z. Liao, S. Banker, L. Thomas, G. A. Salum, K. Merikangis, **J. Goldsmith**, T. Paus, K. Keyes, M. P. Milham (2020).
 Prevalence Of Nonverbal Learning Disability In Three Community Samples
-<i> JAMA Network Open, </i> accepted.
-
-D. Pagliaccio et al (2020+).
-Prenatal Exposure to Polycyclic Aromatic Hydrocarbons Modifies the Effects of Early Life Stress on Attention & Thought Problems in Late Childhood.
-<i> The Journal of Child Psychology and Psychiatry,, </i> accepted.
+<i> JAMA Network Open, </i> 
+<b>3</b> e202551-e202551
 

### 2022-01-23 papers.Rmd
update papers

@@
 
+## 2021
+
+Yan, X., **Goldsmith, J.**, Mohan, S., Turnbull, Z.A., Freundlich, R.E., Billings, F.T., Kiran, R.P., Li, G. and Kim, M. (2021). 
+	Impact of Intraoperative Data on Risk Prediction for Mortality After Intra-Abdominal Surgery. 
+	_Anesthesia \& Analgesia_, **134** 102-113.
+
+Saith, S.E., Gamino, D., Teruya, S., Guadalupe, S., Helmke, S., De Los Santos, J., **Goldsmith, J.**, Rosenblum, H.R., Griffin, J.M. and Maurer, M.S., (2021). 
+	Factors associated with changes in serum transthyretin after treatment with tafamidis and outcomes in transthyretin cardiac amyloidosis.
+	_Amyloid_, **28** 267-268.
+
+Duran, A.T., Pascual, C.B., **Goldsmith, J.**, Howard, V.J., Hutto, B., Colabianchi, N., Vena, J.E., McDonnell, M.N., Blair, S.N., Hooker, S.P. and Diaz, K.M. (2021).
+	Objectively Measured Physical Activity and Sedentary Time Among Adults With and Without Stroke: A National Cohort Study.
+	_Stroke_, **52** e729-e732.
+
+Navas-Acien, A., Domingo-Relloso, A., Subedi, P., Riffo-Campos, A.L., Xia, R., Gomez, L., Haack, K., **Goldsmith, J.**, Howard, B.V., Best, L.G. and Devereux, R., (2021). 
+	Blood DNA Methylation and Incident Coronary Heart Disease: Evidence From the Strong Heart Study. 
+	_JAMA Cardiology_, **6** 1237-1246.
+
+Johnson, C.N., Ramphal, B., Koe, E., Raudales, A., **Goldsmith, J.** and Margolis, A.E., (2021). 
+	Cognitive correlates of autism spectrum disorder symptoms. 
+	_Autism Research_, **14** 2405-2411.
+
+Margolis, A.E., Ramphal, B., Pagliaccio, D., Banker, S., Selmanovic, E., Thomas, L.V., Factor-Litvak, P., Perera, F., Peterson, B.S., Rundle, A.
+Herbstman, J.B., **Goldsmith, J.**, and Rauh, V.
+(2021).
+	Prenatal exposure to air pollution is associated with childhood inhibitory control and adolescent academic achievement. 
+	_Environmental Research_, **202** p 111570.
+
+Nunez, Y., Boehme, A.K., Li, M., **Goldsmith, J.**, Weisskopf, M.G., Re, D.B., Navas-Acien, A., van Donkelaar, A., Martin, R.V. and Kioumourtzoglou, M.A., (2021). 
+	Parkinson's disease aggravation in association with fine particle components in New York State. 
+	_Environmental Research_, **201**, p.111554.
+
+Cornelius, T., Denes, A., Webber, K.T., Guest, C., **Goldsmith, J.**, Schwartz, J.E., and Gorin, A.A. (2021).
+	Relationship quality and objectively measured physical activity before and after implementation of COVID-19 stay-home orders.
+	_Journal of Health Psychology_, DOI:13591053211042075.
+
+C P Friel, C B Pascual, A T Duran, **J Goldsmith**, K M Diaz (2021).
+	Joint associations of occupational standing and occupational exertion with musculoskeletal symptoms in a US national sample.
+	_Occupational and Environmental Medicine_, **78**, 494-499.
+
+Rowland, S.T., Parks, R.M., Boehme, A.K., **Goldsmith, J.**, Rush, J., Just, A.C. and Kioumourtzoglou, M.A., (2021). 
+	The association between ambient temperature variability and myocardial infarction in a New York-State-based case-crossover study: An examination of different variability metrics. 
+	_Environmental Research_, **197**, p.111207.
+
+McDonnell, E.I., Zipunnikov, V., Schrack, J.A., **Goldsmith, J.** and Wrobel, J., (2021). 
+	Registration of 24-hour accelerometric rest-activity profiles and its application to human chronotypes. 
+	_Biological Rhythm Research_, pp.1-21.
+
+Krakauer, J.W., Kitago, T., **Goldsmith, J.**, Ahmad, O., Roy, P., Stein, J., Bishop, L., Casey, K., Valladares, B., Harran, M.D. and Cortes, J.C. (2021). 
+	Comparing a Novel Neuroanimation Experience to Conventional Therapy for High-Dose Intensive Upper-Limb Training in Subacute Stroke: The SMARTS2 Randomized Trial. 
+	_Neurorehabilitation and Neural Repair_, **35**, pp.393-405.
+
+**J Goldsmith**, Y Sun, L Fried, J Wing, G W Miller, K Berhane (2021).
+	The Emergence and Future of Public Health Data Science.
+	_Public Health Reviews_, ** accepted.
+
+Nunez, Y., Gibson, E.A., Tanner, E.M., Gennings, C., Coull, B.A., **Goldsmith, J.**, and Kioumourtzoglou, M.A., (2021). 
+	Reflection on modern methods: good practices for applied statistical learning in epidemiology. 
+	_International journal of epidemiology_, **50**, 685-693.
+
+H Rosenblum, A Masri, D L Narotsky, **J Goldsmith**, N Hamid, R T Hahn, S Kodali, T Vahl, T Nazif, O K Khalique, S Bokhari, P Soman, J L Cavalcante, M S Maurer, A Castano
+	Unveiling outcomes in coexisting severe aortic stenosis and transthyretin cardiac amyloidosis (2021).
+	_European Journal of Heart Failure_, **23** 250-258.
+
+L R Mitrani, J De Los Santos, E Driggin, R Kogan, S Helmke, **J Goldsmith**, A B Biviano, M S Maurer (2021).
+	Anticoagulation with warfarin compared to novel oral anticoagulants for atrial fibrillation in adults with transthyretin cardiac amyloidosis: comparison of thromboembolic events and major bleeding
+	_Amyloid_, **28** 30-34.
+
+S Lovinsky-Desir, K H Jung, M Montilla, J Quinn, J Cahill, D Sheehan, F Perera, S N Chillrud, **J Goldsmith**, M Perzanowski, A Rundle, R Miller (2021).
+	Locations of Adolescent Physical Activity in an Urban Environment and their Associations with Air Pollution and Lung Function.
+	_Annals of the American Thoracic Society_, **18** 84-92.
+
 ## 2020
@@
 
-J Wrobel$^\ddagger$, ML Martin, R Bakshi, PA Calabresi, M Elliot, D Roalf, RC Gur, RE Gur, RG Henry, G Nair, J Oh, N Papinutto, D Pelletier, Daniel Salo Reich, WD Rooney, TD Satterthwaite, W Stern, K Prabhakaran, NL Sicotte, RT Shinohara, \bf J.
-Goldsmith \rm (2020).
+J Wrobel$^\ddagger$, ML Martin, R Bakshi, PA Calabresi, M Elliot, D Roalf, RC Gur, RE Gur, RG Henry, G Nair, J Oh, N Papinutto, D Pelletier, Daniel Salo Reich, WD Rooney, TD Satterthwaite, W Stern, K Prabhakaran, NL Sicotte, RT Shinohara, **J Goldsmith** (2020).
 	Intensity warping for multisite MRI harmonization.
@@
 	<b>34</b> e14028.
-
-L R Mitrani, J De Los Santos, E Driggin, R Kogan, S Helmke, **J Goldsmith**, A B Biviano, M S Maurer (2020). 
-	Anticoagulation with warfarin compared to novel oral anticoagulants for atrial fibrillation in adults with transthyretin cardiac amyloidosis: comparison of thromboembolic events and major bleeding
-	<i> Amyloid, </i> 
-	<b>28</b> 30-34.
-
-H Rosenblum, A Masri, D L Narotsky, **J Goldsmith**, N Hamid, R T Hahn, S Kodali, T Vahl, T Nazif, O K Khalique, S Bokhari, P Soman, J L Cavalcante, M S Maurer, A Castano
-	Unveiling outcomes in coexisting severe aortic stenosis and transthyretin cardiac amyloidosis (2020).
-	<i> European Journal of Heart Failure, </i> 
-	<b>23</b> 250-258.
 
@@
 
-## 2015
+## 2015 and before
 
@@
 | [PubMed](http://www.ncbi.nlm.nih.gov/pubmed/26290354)]
-
-## 2014
 
@@
 
-## 2013
-
 **J. Goldsmith**, S. Greven, C. M. Crainiceanu (2013).
@@
 [PubMed](http://www.ncbi.nlm.nih.gov/pubmed/23885722)]
-
-## 2012
 
@@
 [PubMed](http://www.ncbi.nlm.nih.gov/pubmed/21937920)]
-
-## 2011 and before
 

### 2023-01-05 index.Rmd
ugh typo fix
who has a phone in 2023

@@
 Data science is a newly-formed and, as yet, loosely-defined discipline that has nonetheless emerged as a critical component of successful research in biostatistics and public health.
-I work to incorporate data science techniques for transparency and reproducibiity into biostatistical analyses.
+I work to incorporate data science techniques for transparency and reproducibility into biostatistical analyses.
 Research projects are accompanied by robust, publicly available software and analytical pipelines that ensure the reproducibility of the results.
@@
 Email: [jeff.goldsmith@columbia.edu](mailto:jeff.goldsmith@columbia.edu)
-Phone: 212-342-4599

### 2025-02-26 index.Rmd
small updates
update bio etc

@@
 
-Associate Professor of Biostatistics <br>
-Columbia University Mailman School of Public Health
-
 <br><img src="images/jeff.jpg" alt="jeff" style="width:65%; border:10px solid"><br>
-
-#### Research
-
-For several years, I have worked to advance the state-of-the-art in functional data analysis by developing methods for understanding patterns in large, complex datasets in neuroscience, physical activity monitoring, and other areas.
-
-Working closely with clinicians and neuroscientists around the world, my collaborators and I have focused on improving the understanding skilled movements.
-This work involves reaching movements made by stroke patients: in these experiments, a patient's fingertip position is recorded hundreds of time per second for the duration of the reach.
-I have developed new statistical methods to understand the impact of stroke on movement quality, and applied these to large, longitudinal datasets.
-In parallel, I have proposed methods for wearable device research, especially focusing on accelerometers.
-These devices can produce minute-by-minute (or even finer) resolution observations of activity for hundreds of participants over several days, weeks, or months.
-The methods developed include approaches for regression with activity trajectories as outcomes; for interpretable dimension reduction; and for aligning major patterns (like wake from sleep, mid-day dips in activity, and sleep onset) across subjects.
-
-#### Data science
-
-Data science is a newly-formed and, as yet, loosely-defined discipline that has nonetheless emerged as a critical component of successful research in biostatistics and public health.
-I work to incorporate data science techniques for transparency and reproducibility into biostatistical analyses.
-Research projects are accompanied by robust, publicly available software and analytical pipelines that ensure the reproducibility of the results.
-This approach is informed by my work in developing a graduate course in [data science](https://p8105.com).
 
@@
 
-I received a BS in mathematics from [Dickinson College](http://www.dickinson.edu) in 2007 and a PhD in Biostatistics from [Johns Hopkins University](http://www.jhsph.edu/departments/biostatistics/) in 2012.
-My dissertation was advised by [Ciprian Crainiceanu](http://www.biostat.jhsph.edu/~ccrainic/) and [Brian Caffo](https://sites.google.com/view/bcaffo/home), and focused on statistical methods for high-dimensional structured data.
-I joined Columbia as an assistant professor in 2012.
+Dr.
+Jeff Goldsmith is Associate Professor of Biostatistics at the Columbia University Mailman School of Public Health.
+He serves as the Associate Dean for Data Science at MSPH, and as the Associate Director for Education at the Columbia University Data Science Institute.
+His statistical work focuses on functional data analysis specifically and high-dimensional, structured data more broadly.
+He has developed new statistical methods for regression, dimension reduction, and unsupervised learning.
+Dr.
+Goldsmith has a broad methodological and collaborative research portfolio, encompassing neuroscience and neuroimaging, physical activity behaviors, environmental health, and cardiovascular health.
+He has published in a range of outlets, including Biostatistics, Biometrics, Journal of the American Statistical Association, eLife, and Neurorehabilitation and Neural Repair; and he is coauthor of the book Functional Data Analysis with R.
 
-In 2013, I founded (with [Todd Ogden](https://www.mailman.columbia.edu/people/our-faculty/to166) and [Phil Reiss](https://works.bepress.com/phil_reiss/)) the Functional Data Analysis Working Group ([FDAWG](https://www.mailman.columbia.edu/research/functional-data-analysis-working-group)) at Columbia Biostat.
+Dr.
+Goldsmith is a Fellow of the American Statistical Association and was selected as an inaugural recipient of the COPSS Emerging Leader Award.
+He received the Mailman School's Dean's Excellence in Leadership Award the Columbia University Presidential Award for Outstanding Teaching.
+
+He works to incorporate data science techniques for transparency and reproducibility into biostatistical analyses.
+Research projects are accompanied by robust, publicly available software and analytical pipelines that ensure the reproducibility of the results.
+This approach is informed by his work in developing a graduate course in [data science](https://p8105.com).
+
+In 2013, Dr.
+Goldsmith founded (with [Dr.
+Todd Ogden](https://www.mailman.columbia.edu/people/our-faculty/to166) and [Dr.
+Phil Reiss](https://works.bepress.com/phil_reiss/)) the Functional Data Analysis Working Group ([FDAWG](https://www.mailman.columbia.edu/research/functional-data-analysis-working-group)) at Columbia Biostat.
+
+Dr.
+Goldsmith received a BS in mathematics from [Dickinson College](http://www.dickinson.edu) in 2007 and a PhD in Biostatistics from [Johns Hopkins University](http://www.jhsph.edu/departments/biostatistics/) in 2012.
 
@@
 New York, New York 10032
-
-Email: [jeff.goldsmith@columbia.edu](mailto:jeff.goldsmith@columbia.edu)

### 2025-02-26 teaching.Rmd
typo fix
update bio etc

@@
 
-Fall 2019: [Data Science I](http://p8105.com)
+2017-2024: [Data Science I](http://p8105.com)
 
@@
 
-Fall 2018: [Data Science I](http://p8105.com)  
-Fall 2017: [Data Science I](http://p8105.com)  
 Spring 2016: [Linear Regression Models](http://jeffgoldsmith.com/P8111/)  

### 2025-02-26 tidyfun.Rmd
link to right page
tidyfun + CV update
update bio etc

@@
 
-This page hosts a presentation / quick intro to [`tidyfun`](https://fabian-s.github.io/tidyfun/) -- enjoy!
+This page hosts a presentation / quick intro to [`tidyfun`](https://tidyfun.github.io/tidyfun/) -- enjoy!
 
@@
 
-For illustration, we plot the vector `cca_five` below.
-
-```{r, ex-fig}
-plot(cca_five)
-```
-
 Converting "raw" to "basis" representation is possible, and introduces some smoothing by default.
@@
   tfb()
-```
-
-A quick plot illustrates the difference visually; lots of things are different in the background!
-
-```{r}
-plot(cca_five)
-lines(cca_five_b, col = "red")
 ```
@@
   gglasagna(
-    y = cca, 
+    tf = cca, 
     order = tf_integrate(cca, definite = TRUE), 
@@
 
-## Some FPCA
-
-```{r}
-# irregular data 
-data(dti_df)
-dti_fpca = rfr_fpca(Y = "cca", data = dti_df)
-
-dti_df %>% 
-  modelr::add_predictions(dti_fpca, var = "cca_fits") %>% 
-  filter(case == "control") %>% 
-  ggplot(aes(y = cca_fits)) + 
-  geom_spaghetti(alpha = .4) + 
-  geom_spaghetti(aes(y = cca), color = "blue", alpha = .3) + 
-  facet_grid(~sex)
-```
-
 ## Next steps
